---
title: "Cleandata_before_preprocessing"
author: "Yiming Qian"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: hide
params:
  data_path: "~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/raw_data"
  contrast_raw_path: "contrast_sensitivity_task_data"
  motion_raw_path: "motion_temporal_threshold_data"
  qualtrics_csv_dir: "qualtrics_survey_data/csv"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)

library(tidyverse) # for pipe
```

# Import motion threshold

```{r list-files}
fpm <- file.path(params$box_path, params$motion_raw_path)

if (dir.exists(fpm)) {
  flm <- list.files(fpm, pattern = "\\.csv$", full.names = TRUE)
  fm <- fl[stringr::str_detect(flm, "motion")]
} else {
  stop(paste0("No data files in '", fpm, "'."))
}
```

There are `r dim(fm)` motion duration threshold files to visualize.
```{r list-files}
fpc <- file.path(params$box_path, params$contrast_raw_path)

if (dir.exists(fpc)) {
  flc <- list.files(fpc, pattern = "\\.csv$", full.names = TRUE)
  fc <- fl[stringr::str_detect(flc, "motion")]
} else {
  stop(paste0("No data files in '", fpc, "'."))
}
```
There are `r dim(fm)` motion duration threshold files to visualize.

# clean the data-motion
# The goal is  to get the motion data (actual trials) from all the participants in one dataset
```{r import-as-df}
import_clean_motion_data <- function(fn) {
  df <- readr::read_csv(fn)
  df <- dplyr::mutate(df, p_id = extract_sub_id_from_fn(fn),
                      run = run_n + 1)
  df <- dplyr::mutate(df, corr = correct, dur_s = FWHM)
  df <- dplyr::select(df,
                      p_id,
                      run,
                      trial_n,
                      dur_s,
                      corr,
                      rt)
  df <- dplyr::mutate(df, run = ordered(run))
  
  df
}
```

```{r bulk-import}
m_df <- purrr::map_dfr(fm, import_clean_motion_data)
```
```{r}
# fix the QA-failed data

```
```{r save}
# save the data
```
# clean and aggregate the data-contrast
# The goal is to get the contrast data (actual trials) from all the participants in one dataset
```{r import-as-df}
import_clean_contrast_data <- function(fn) {
  df <- readr::read_csv(fn)
  df <- dplyr::mutate(df, p_id = extract_sub_id_from_fn(fn),
                      run = run_n + 1)
  df <- dplyr::mutate(df, corr = correct, dur_s = FWHM)
  df <- dplyr::select(df,
                      p_id,
                      run,
                      trial_n,
                      dur_s,
                      corr,
                      rt)
  df <- dplyr::mutate(df, run = ordered(run))
  
  df
}
```


```{r bulk-import}
c_df <- purrr::map_dfr(fm, import_clean_contrast_data)
```
```{r}
# fix the QA-failed data

```
```{r save}
# save the data
```

# clean and aggregate the two qualtrics data
# The goal is to get the the qualtrics data of all the participants in one dataset and delete the practice one.
```{r}
qualtrics_dir <- "~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/qualtrics_survey_data"
qualtrics_zip_dir <- paste0(qualtrics_dir, "/", "zip")
qualtrics_zip_fns <- list.files(qualtrics_zip_dir, pattern = "\\.zip$", full.names = TRUE)
lapply(qualtrics_zip_fns, unzip, exdir = paste0(qualtrics_dir, "/csv"))
```

```{r}
qualtrics_csv_dir <- paste0(qualtrics_dir, "/", "csv")
# Just pick 1st 1st one for now

qualtrics_fns <- list.files(qualtrics_csv_dir, pattern = "\\.csv$", full.names = TRUE)
this_fn <- qualtrics_fns[1]
qualtrics_df <- readr::read_csv(this_fn)


# Trim first two rows
n_rows <- dim(qualtrics_df)[1]
qualtrics_trim <- qualtrics_df[3:n_rows,]
```

```{r}
# fix the QA-failed data

```
```{r}
# merge the dataset
q_df
```

```{r save}
# save the data
```