---
title: "Outliner"
author: "Yiming Qian"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: hide
params:
  this_contr_csv_fn: "~/Box/Project_Sex_difference_on_Motion_Perception/data/raw_data/contrast_sensitivity_task_data/2019111309492663_contrast_sensitivity_task.csv"
  this_motion_dur_csv_fn: "~/Box/Project_Sex_difference_on_Motion_Perception/data/raw_data/motion_temporal_threshold_data/2019111309492663_motion_temporal_threshold.csv"
  this_sub_id: "2019111309492663"
  data_path: "~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/raw_data"
  contrast_raw_path: "contrast_sensitivity_task_data"
  motion_raw_path: "motion_temporal_threshold_data"
  qualtrics_csv_dir: "qualtrics_survey_data/csv"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

# Possible outliners
1. 2 visual perception tasks: we will get accuracy, rts. Based on the accuracy data, we will calculate 4 thresholds of 4 runs t in each experiment, the visual parameter. Then, the averaged threshold, in which the participant were estimated to have 80% accuracy, will be gotten from the median of these 4 threshold.
    - Within-subject: accuracy will not be missing. But if the whole run did not reach the 80% accuracy, which means more than 6 errors in 30 trials, I am thinking whether to discard this run? One solution is to detect the outliners from these 4 threshold by 2 SD (We need to see how it works). We will detect the outliners of Rts by 2 SD within participant.  
    - Between-subject: we will detect the outliners of the final threshold with the decision rule of 2 SD, but not mean RTs, within male groups and female groups, due to our research questions. 
2. qualtrics:
    - within-subject: the participant may answer randomly or choose the same answer in all hobbies.
    - between-subject: we will detect the outliners of the verbal ability, spatial ability and male-types hobbies using 1.96 SD, within male groups and female groups, due to our research questions.. 

# Currently it is only for one participant
# single participant check
### Import
```{r}
s_data <- readr::read_csv(params$this_contr_csv_fn)
s1_clean <- s_data %>%
  mutate(., correctAns = stringr::str_extract(correctAns, "left|down|right|up")) %>%
  mutate(., corr = if_else(resp == correctAns, 1, 0)) %>%
  rename(., contr = loop_trial.intensity,
         trial_n = loop_trial.thisN)

s1_subset <- s1_clean %>%
  dplyr::select(., Participant, Gender,
                trial_n,
                contr,
                correctAns,
                resp,
                corr,
                resp.rt) %>%
  dplyr::filter(., trial_n >= 0) %>%
  dplyr::mutate(run = rep(1:4, each=30))
```
```{r contrast-sensitivity-by-trial}
## visual check
s1_subset %>% ggplot(.) +
  aes(x = trial_n, y = contr) +
  facet_grid(. ~ run) +
  geom_smooth() +
  geom_point() +
  ggtitle("Contrast sensitivity data")
```
# qualtrics
```{r same_answer}
## detect the participants with more than 50% same answer

```
```{r random-choice}
## visual check
```




# all participants
# import
```{r list-files}
m_df
c_df
```
```{r threshold}
## calculate the threshold in each run


thres
```


```{r within-subject-threshold}
thres_outlier_within_subject <- thres %>%
  map_df(., function(x){
    if (!is.numeric(x)) { return(rep(FALSE, length(x))) } #don't filter any non-numeric columns
    ifelse(x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x), TRUE, FALSE)
  })  # we mark it to make decision
```

```{r within-subject-rt}
rt_outlier_within_subject <- data %>%
  map_df(., function(x){
    if (x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x)) { x=NA } #don't filter any non-numeric columns
  } # we can change it to NA
```

```{r}
# calculate the final threshold
median()
```
```{r between-subject-threshold}
rt_outlier_between_subject <- data %>%
  map_df(., function(x){
    if (!is.numeric(x)) { return(rep(FALSE, length(x))) } #don't filter any non-numeric columns
    ifelse(x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x), TRUE, FALSE) # we mark it to make decision
```
```{r between-subject-rt}
rt_outlier_between_subject <- data %>%
  map_df(., function(x){
    if (!is.numeric(x)) { return(rep(FALSE, length(x))) } #don't filter any non-numeric columns
    ifelse(x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x), TRUE, FALSE) # we mark it to make decision
```

# qualtics
# import the unprocessed dataset
```{r}
q_df
```
```{r}
# check whether there areall A-E across answers in hobbies

```
```{r}
# check how many items are answered

```
```{r}
# random choice

```
```{r}
# same answer, how many conservative rows are the same answer

```
```{r}
# visual check

```

# import the processed dataset
```{r}

```

# if any test have 0 score, double check
```{r}
data[A==0]<-NA
```

```{r between-subject-qualtrics}
# detect outlier 2SD within gender group
male_outlier_within_subject <- data %>%
  filter(gender=="male")
  map_df(., function(x){
    if (!is.numeric(x)) { return(rep(FALSE, length(x))) } #don't filter any non-numeric columns
    ifelse(x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x), TRUE, FALSE) # we mark it to make decision
female_outlier_between_subject <- data %>%
  filter(gender=="female")
  map_df(., function(x){
    if (!is.numeric(x)) { return(rep(FALSE, length(x))) } #don't filter any non-numeric columns
    ifelse(x >= mean(x)+2*sd(x) | x <= mean(x)-2*sd(x), TRUE, FALSE) # we mark it to make decision
```