---
title: "Individual differences in visual perception in adults"
author: "Rick Gilmore, Yiming Qian, & Andrea Seisler"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    self_contained: false
    code_folding: hide    
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document serves as the master protocol for the study.

# IRB

This protocol, "Individual differences in visual perception in adults," has been assigned protocol number 13345.
The most recent IRB approval was granted on 2010-10-14.
Files related to the approved (exempt) submission can be found [here](../irb/2019-10-24).

# Equipment preparation

```{r, child="calibrate-monitor.Rmd"}
```

# Survey preparation

This study uses Qualtrics to collect implied/oral consent and other data from participants.
The URL for the survey is 

# Scheduling participants

Rick Gilmore is the PI on the SONA Systems study associated with this protocol.
Yiming Qian and Andrea Seisler are researchers.
The URL is <https://pennstate.sona-systems.com/exp_info.aspx?experiment_id=2587>.

The process of scheduling participants involves the following steps:

DESCRIBE STEPS

# Day of visit

```{r, child="sex-differences-setup.Rmd"}
```

# Data processing

# Appendices

```{r terminology, child="terminology.Rmd"}
```

```{r parameters, child="parameters.Rmd"}
```
