---
title: "Individual differences in visual perception in adults"
author: "Rick Gilmore, Yiming Qian, & Andrea Seisler"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    self_contained: false
    code_folding: hide    
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document serves as the master protocol for the study.

# IRB

This protocol, "Individual differences in visual perception in adults," has been assigned protocol number 13345.
The most recent IRB approval was granted on 2010-10-14.
Files related to the approved (exempt) submission can be found [here](../irb/2019-10-24).

# Prior to data collection start

## Equipment preparation

First, we need to do benchmark testing to determine what screen resolution will work at the highest temporal resolution (120 Hz).
This study requires high temporal resolution in order to measure temporal thresholds--the shortest stimulus duration that participants require in order to accurately detect the direction of motion.

Once we have determined the best monitor settings, we will calibrate the monitor before we start collecting data.
Those steps follow.

```{r, child="calibrate-monitor.Rmd"}
```

We may check the monitor calibration during data collection at a frequency we will decide later.

## Survey preparation

This study uses Qualtrics to collect implied/oral consent and other data from participants.
Yiming has generated a draft survey.
She will export it as `*.qsf`, and Rick will import it into his own Qualtrics account.
Rick will also publish the survey.

The URL for the survey is **SURVEY URL HERE**

# Scheduling participants

Rick Gilmore is the PI on the SONA Systems study (Study ID 2587) associated with this protocol.
Yiming Qian and Andrea Seisler are researchers.
The URL is <https://pennstate.sona-systems.com/exp_info.aspx?experiment_id=2587>.

The process of scheduling participants involves the following steps:

1. Create slots on SONA with specific dates and times
2. When slot is scheduled, email sent to Yiming and Andrea.
3. Scheduled slots will be added to lab calendar.
4. Researchers will be contacted **HOW** if they are needed for a slot that is not part of their regularly scheduled lab time.

## Weekly testing slots

| Day of Week | Time    | Researcher(s)      | Lead   |     
|-------------|---------|--------------------|--------|
| Mon         | 10a     | Sandy, Emily       | Andrea |
|             | 11a     | Sandy, Emily, Amar | Yiming |
|             | 1p      |                    | Yiming |
|             | 2p      |                    | Yiming |
|             | 3p      |                    | Yiming |
|             | 4p      |                    | Yiming |
| Tue         | 9a      |                    | Andrea |
|             | 10a     |                    | Andrea |
|             | 11a     | Amar, Michelle     | Andrea |
|             | 12p     | Michelle, Joseph   |        |
|             | 1p      | Michelle, Luka     |        |
| Wed         | 10a     | Sandy, Rachel, Amar |       |
|             |         | Sandy, Rachel, Amar, Emily | |
| Thu         | 9a      | Joseph, Michelle, Luka | |
|             | 12p     | Amar                      | |
| Fri         | 9a      | Rachel                    | |
|             | 10a     | Rachel, Emily             | |
|             | 11a     | Rachel, Emily             | |
|             | 12p     | Emily                     | |

# Day of visit

```{r, child="sex-differences-setup.Rmd"}
```

# Data processing

## Gathering

1. Computer task data
2. Qualtrics data

## Validation and cleaning

## Visualization

## Analysis

# Appendices

```{r terminology, child="terminology.Rmd"}
```

```{r parameters, child="parameters.Rmd"}
```
