---
title: "Qualtrics munging from the CSV"
author: "Rick Gilmore"
date: "`r Sys.time()`
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Alternative approach

This document describes an alternative approach to downloading and cleaning the Qualtrics survey data for the Sex Differences in Visual Perception project.

## Manually download the data file

The data file must be exported from Qualtrics.

## Open the data file

The `*.zip` data file(s) can be found at

`~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/qualtrics_survey_data/zip`

The following code unzips any target `.zip` files and copies it to 

`~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/qualtrics_survey_data/csv`

```{r}
qualtrics_dir <- "~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/qualtrics_survey_data"
qualtrics_zip_dir <- paste0(qualtrics_dir, "/", "zip")
qualtrics_zip_fns <- list.files(qualtrics_zip_dir, pattern = "\\.zip$", full.names = TRUE)
lapply(qualtrics_zip_fns, unzip, exdir = paste0(qualtrics_dir, "/csv"))
```

```{r}
qualtrics_csv_dir <- paste0(qualtrics_dir, "/", "csv")
# Just pick 1st 1st one for now

qualtrics_fns <- list.files(qualtrics_csv_dir, pattern = "\\.csv$", full.names = TRUE)
this_fn <- qualtrics_fns[1]
qualtrics_df <- readr::read_csv(this_fn)


# Trim first two rows
n_rows <- dim(qualtrics_df)[1]
qualtrics_trim <- qualtrics_df[3:n_rows,]
```

## Extract specific data types

### Demographics

```{r}
demog_df <- qualtrics_trim %>%
  dplyr::filter(., !is.na(`Participant ID`)) %>%
  dplyr::rename(p_id = `Participant ID`) %>%
  dplyr::rename(vis_acuity = `Q81`) %>%
  dplyr::rename(gender = `Q1`) %>%
  dplyr::rename(age_yrs = `Q4`) %>%
  dplyr::rename(school_yr = `Q2`) %>%
  dplyr::rename(major = `Q3`) %>%
  dplyr::rename(ethnicity = `Q89`) %>%
  dplyr::rename(preferred_hand = `Q88`) %>%
  dplyr::rename(stereo_vision = `Q92`) %>%
  dplyr::rename(color_p6 = `Q93_1`) %>%
  dplyr::rename(color_p7 = `Q93_2`) %>%
  dplyr::rename(color_p8 = `Q93_3`) %>%
  dplyr::select(p_id, gender, vis_acuity, age_yrs, school_yr,
                major, ethnicity, preferred_hand, stereo_vision,
                color_p6, color_p7, color_p8)

# Some cleaning

demog_df <- demog_df %>%
  dplyr::mutate(., p_id = stringr::str_remove_all(p_id, "[:-]"))

demog_df %>%
  dplyr::select(., p_id, gender, vis_acuity) %>%
  knitr::kable(.)
```

