---
title: "Post-processing Quality Assurance (QA)"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
params:
  box_path: "~/Box"
  data_path: "/Project_Sex_difference_on_Motion_Perception/data"
  contrast_raw_path: "/raw_data/contrast_sensitivity_task_data"
  motion_raw_path: "/raw_data/motion_temporal_threshold_data"
  passed_qa_path: "/passed_qa"
  failed_qa_path: "/failed_qa"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE,
                      message = FALSE)

# Manage package dependencies
if (!require(pacman)) {
  install.packages("pacman")
}

library(tidyverse)
library(qualtRics)
```

# Purpose

This script describes the process for doing quality assurance (QA) review on each session, focusing on the computer based tasks.

To render, enter `rmarkdown::render("analysis/session_qa.Rmd", params = list(box_path = "<YOUR_BOX_PATH>"))`, substituting the path to your Box folder on your local machine.
On Mac OS the default is "~/Box".

# Background

1. There are two data files for each participant:
  - One for the Abramov et al contrast sensitivity task:
      - `r paste0(params$box_path, params$data_path, params$contrast_raw_path)`
  - One for the Murray et al temporal threshold task 
      - `r paste0(params$box_path, params$data_path, params$motion_raw_path)`
2. Each data file contains information about the four runs, each run consisting of $n=30$ trials.
3. The computer-based tasks record the participant gender.
4. The data files record the participant ID and the participant ID *should* match the initial portion of the file name.
5. The data files include the most essential variables for analysis.

## QA steps

1. For each of the computer task
  - List the `*.csv` files in the data directory
  - Look inside the files and determine the following:
      - Does the participant ID match the ID in the file name?
      - Is the participant ID in the file?
      - Does the file have enough trials ($n=30$ for 4 runs)?
      - Does the file have the key variables needed for analysis?
      - Does the file include a variable for gender?
  - If the answer to all of these questions is yes, then
      - Copy the file(s) to a `pass_qa` folder:
          - `r paste0(params$box_path, params$data_path, params$passed_qa_path)`
  - If the answer is no, then
      - Copy the file(s) to a `fails_qa` folder:
          - `r paste0(params$box_path, params$data_path, params$failed_qa_path)`
2. A separate R Markdown document should address the file(s) that fail QA. 
If the failures can be addressed, the document should do so and then copy the corrected data file to the `pass_qa` folder.

# Implementation

## Create lists of `.csv` files

### Contrast

```{r contrast-csvs}
contr_data_path <- paste0(params$box_path, 
                          params$data_path, 
                          params$contrast_raw_path)
if (dir.exists(contr_data_path)) {
  contrast_csvs <- list.files(contr_data_path, pattern = "\\.csv$")
  contrast_csvs %>% 
    knitr::kable(.)
} else {
  message(paste0("No data files exist in ", contr_data_path))
}
```

There are `r length(contrast_csvs)` .csv files for the Abramov contrast sensitivity task.

### Motion

```{r motion-csvs}
motion_data_path <- paste0(params$box_path, 
                           params$data_path, 
                           params$motion_raw_path)
if (dir.exists(motion_data_path)) {
  motion_csvs <- list.files(motion_data_path, pattern = "\\.csv$")
  motion_csvs %>% knitr::kable(.)  
} else {
  message(paste0("No data files exist in ", motion_data_path))
}

```

There are `r length(motion_csvs)` .csv files for the Murray motion temporal threshold task.

## File by file QA

```{r define-qa-functions}
has_enough_trials <- function(data_df, n_trials = 4*30) {
  dim(data_df)[1] >= n_trials
}

observer_id_in_file <- function(data_df, task='contr') {
  if (task=='contr') {
    sum(!(is.na(data_df$Participant))) == length(data_df$Participant)
  } else {
    sum(!(is.na(data_df$observer))) == length(data_df$observer)
  }
}

gender_in_file <- function(data_df, task = 'contr') {
  if (task == 'contr') {
    sum(!(is.na(data_df$Gender))) > 0    
  } else {
    sum(!(is.na(data_df$gender))) > 0 
  }
}

sub_id_matches_fn <- function(data_fn, task='contr') {
  data_df <- readr::read_csv(data_fn)
  if (task=='contr') {
    sub_id <- as.character(data_df$Participant)
  } else {
    sub_id <- as.character(data_df$observer)
  }
  sub_id_fn <- stringr::str_extract(basename(data_fn), "[0-9]+")
  sum(sub_id == sub_id_fn) == length(sub_id)
} 

essential_vars_in_file <- function(data_df, task = 'contr') {
  if (task == 'contr') {
    essential_vars <- c("correctAns", "loop_trial.intensity", 
                        "loop_trial.thisN", "Participant", "Gender", "resp.rt")
  } else {
    essential_vars <- c("run_n", "correct", 
                        "trial_n", "stim_secs", "correct", 
                        "rt", "observer", "FWHM", "actual_frame")
  }
  (sum(essential_vars %in% names(data_df)) == length(essential_vars))
}

make_qa_df <- function(data_fn, task = 'contr') {
  fn <- basename(data_fn)
  data_df <- readr::read_csv(data_fn)
  data.frame(fn,
             id_matches_fn = sub_id_matches_fn(data_fn, task),
             id_in_file = observer_id_in_file(data_df, task),
             enough_trials = has_enough_trials(data_df),
             has_key_vars = essential_vars_in_file(data_df, task),
             gender_var = gender_in_file(data_df, task)
             )
}
```

### Contrast

```{r contr-fns}
contr_fns <- list.files(contr_data_path, 
                        pattern = "\\.csv$", full.names = TRUE)
dfl <- lapply(contr_fns, make_qa_df, task = "contr")
contrast_file_qa <- Reduce(function(x,y) merge(x,y, all=TRUE), dfl)
contrast_file_qa %>% 
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

### Motion

```{r}
motion_fns <- list.files(motion_data_path, 
                         pattern = "\\.csv$", full.names = TRUE)
dfl <- lapply(motion_fns, make_qa_df, task = "motion")
motion_file_qa <- Reduce(function(x,y) merge(x,y, all=TRUE), dfl)
motion_file_qa %>% 
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

## Examine files that pass or fail QA

### Files that pass QA

```{r}
motion_file_qa <- motion_file_qa %>%
  dplyr::mutate(., pass_qa = id_matches_fn & 
                  id_in_file & enough_trials & 
                  has_key_vars & gender_var)

contrast_file_qa <- contrast_file_qa %>%
  dplyr::mutate(., pass_qa = id_matches_fn & 
                  id_in_file & enough_trials & 
                  has_key_vars & gender_var)
```

#### Contrast task

There are `r sum(contrast_file_qa$pass_qa)` contrast task files that pass file-level QA.

#### Motion task

There are `r sum(motion_file_qa$pass_qa)` motion task files that pass file-level QA.

### Files that fail QA

#### Contrast task

There are `r sum(!contrast_file_qa$pass_qa)` contrast task files that fail file-level QA.

```{r}
contrast_file_qa %>%
  dplyr::filter(., !pass_qa) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")

```

#### Motion task

There are `r sum(!motion_file_qa$pass_qa)` motion task files that fail file-level QA.

```{r}
motion_file_qa %>%
  dplyr::filter(., !pass_qa) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

## Copy files

Copy files to directories based on whether the files pass or fail QA review.

```{r, message=FALSE, warning=FALSE, include=FALSE}
# generate full file path to target directory
passed_qa_full_path <- paste0(params$box_path, params$data_path, params$passed_qa_path)
passed_qa_full_path

# Add full file paths to data frames
motion_file_qa <- motion_file_qa %>%
  dplyr::mutate(., full_path = paste0(motion_data_path, "/", fn)) %>%
  dplyr::mutate(., qa_full_path = paste0(params$box_path, params$data_path,
                                         params$passed_qa_path, "/", fn)) %>%
  dplyr::mutate(., failed_qa_full_path = paste0(params$box_path, params$data_path,
                                         params$failed_qa_path, "/", fn))

contrast_file_qa <- contrast_file_qa %>%
  dplyr::mutate(., full_path = paste0(contr_data_path, "/", fn)) %>%
  dplyr::mutate(., qa_full_path = paste0(params$box_path, params$data_path,
                                         params$passed_qa_path, "/", fn)) %>%
  dplyr::mutate(., failed_qa_full_path = paste0(params$box_path, params$data_path,
                                         params$failed_qa_path, "/", fn))

# Helper function to handle copying
copy_files_to_qa_target <- function(df_i, df) {
  if (df$pass_qa[df_i]) {
    file.copy(from = df$full_path[df_i], df$qa_full_path[df_i], overwrite = TRUE)
  } else {
    file.copy(from = df$full_path[df_i], df$failed_qa_full_path[df_i], overwrite = TRUE)
  }
}

# Now copy
purrr::map(1:dim(motion_file_qa)[1], copy_files_to_qa_target, motion_file_qa)
purrr::map(1:dim(contrast_file_qa)[1], copy_files_to_qa_target, contrast_file_qa)
```

