---
title: "Aggregate & Visualize Contrast Task"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: hide
params:
  box_path: "~/Box Sync"
  data_path: "/Project_Sex_difference_on_Motion_Perception/data"
  passed_qa_path: "/passed_qa"
  failed_qa_path: "/failed_qa"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
```

# Purpose

This document aggregates the individual CSV data files from the Abramov contrast sensitivity task and presents visualizations of them.

# Set-up

This document takes as input parameters the path components to the CSV files that have passed QA.
For example, on a typical Mac OS installation, the path would be as follows:

- `r paste0(box_path, data_path, passed_qa)`

## Source helper functions

```{r}
read_indiv_file <- function(fn) {
  message(paste0("Reading data for '", fn, "'."))
  s_data <- readr::read_csv(fn)
  s_data
}

drop_practice <- function(df) {
  dplyr::filter(df, !is.na(loop_trial.thisN))
}

select_key_vars <- function(df) {
  dplyr::select(df, Participant, Gender, 
                loop_trial.thisN, 
                loop_trial.intensity,
                correctAns,
                resp,
                ori,
                resp.rt)
}

clean_rename_df <- function(df) {
  df <- dplyr::mutate(df, 
                      correctAns = stringr::str_extract(correctAns,
                                                        "left|down|right|up"),
                      corr = if_else(resp == correctAns, 1, 0)) %>%
    dplyr::rename(., contr = loop_trial.intensity,
                  trial_n = loop_trial.thisN) %>%
    dplyr::select(., Participant, Gender,
                  trial_n,
                  contr,
                  correctAns,
                  resp,
                  corr,
                  resp.rt) %>%
    dplyr::mutate(run = rep(1:4, each=30))

  df
}

read_clean_df <- function(fn) {
  df <- read_indiv_file(fn)
  df <- df %>%
    drop_practice(.) %>%
    select_key_vars(.) %>%
    clean_rename_df(.)
  df
}
```

# Aggregate individual CSVs

## Generate file list

```{r}
path_2_data <- "~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/passed_qa"
#path_2_data <- paste0(box_path, data_path, passed_qa)

data_files <- list.files(path_2_data, pattern = "contrast",
                         full.names = TRUE)
```

## Import all files in list

```{r}
data_agg <- purrr::map_dfr(data_files[1:64], read_clean_df)
```

