---
title: "get_new_hobby_var"
author: "Yiming Qian"
date: "3/4/2021"
output: 
  html_document:
    self_contained: yes
    code_folding: hide
params:
  contr_csv_fn: "contrast_output_Oct2020.csv"
  motion_csv_fn: "motion_output_Oct2020.csv"
  qualtrics_csv_fn: "qualtrics_output_10_14_2020.csv"
  this_sub_id: "2019111309492663"
  data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/raw_data"
  output_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  contrast_raw_path: "contrast_sensitivity_task_data"
  motion_raw_path: "motion_temporal_threshold_data"
  csv_fn: "combined_2021-02-16.csv"
  outlier_sd_thresh: 3.0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# use discriminitation analysis to get a new variable "hobby"
### discrimination analysis
#### get the data
```{r}
qua_raw <- readr::read_csv(file.path(params$data_path, "qualtrics_output_10_14_2020.csv")) 
hobby_name<-readr::read_csv(file.path(params$hobby_data_path, "hobbies_names.csv")) 

# rename variables
names(qua_raw)[177:236] <- hobby_name$new_name
qua_raw$participant[which(qua_raw$participant=="2019-11-1309:49:2632")]<-101
qua_raw$participant[which(qua_raw$participant=="2019-11-1311:10:2438")]<-102
qua_raw$participant[which(qua_raw$participant=="2019-11-1313:38:0337")]<-103
qua_raw$participant[which(qua_raw$participant=="2019-11-1314:56:0233")]<-105
qua_raw$participant[which(qua_raw$participant=="2019-11-1316:12:1898")]<-107

qua_raw$participant[which(qua_raw$participant=="2019-11-1808:39:3927")]<-104
qua_raw$participant[which(qua_raw$participant=="2019-11-1811:26:4976")]<-109
qua_raw$participant[which(qua_raw$participant=="2019-11-1812:45:1738")]<-111
qua_raw$participant[which(qua_raw$participant=="2019-11-1813:58:0893")]<-113
qua_raw$participant[which(qua_raw$participant=="2019-11-1814:48:2896")]<-106

qua_raw$participant[which(qua_raw$participant=="2019-11-2013:40:1983")]<-115
qua_raw$participant[which(qua_raw$participant=="2019-11-2014:53:2351")]<-108
qua_raw$participant[which(qua_raw$participant=="2019-11-2016:11:0713")]<-117
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/2019 11:14")]<-119
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/2019 12:17")]<-110

qua_raw$participant[which(qua_raw$RecordedDate=="11/21/2019 13:54")]<-121
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/2019 10:45")]<-123
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/2019 11:30")]<-125
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/2019 14:35")]<-127
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/2019 16:52")]<-320

qua_raw$participant[which(qua_raw$RecordedDate=="11/22/2019 17:40")]<-112
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/2019 12:05")]<-114
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/2019 14:36")]<-129
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/2019 16:44")]<-324
qua_raw$participant[which(qua_raw$RecordedDate=="12/5/2019 9:59")]<-116

qua_raw$participant[which(qua_raw$RecordedDate=="12/5/2019 13:20")]<-131
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/2019 13:23")]<-118
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/2019 14:29")]<-133
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/2019 15:44")]<-120
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/2019 16:44")]<-330

qua_raw$participant[which(qua_raw$RecordedDate=="12/12/2019 17:45")]<-135
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/2019 13:58")]<-122
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/2019 14:47")]<-124
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/2019 16:32")]<-137
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/2019 17:04")]<-139

qua_raw$participant<-as.numeric(qua_raw$participant)
qua_raw$sex<-factor(qua_raw$sex, levels=c(2,1), labels=c("Females","Males"))
hobbies<-qua_raw[,c(7,18,20,177:236, 276,277)] %>%
  filter(Finished==1) %>%
  filter(participant!="test") %>%
  filter(participant!=0) 
hobby<-hobbies[,-c(1,2,64,65)]
```

#### Linear discriminant analysis - LDA

The LDA algorithm starts by finding directions that maximize the separation between classes, then use these directions to predict the class of individuals. These directions, called linear discriminants, are a linear combinations of predictor variables.

LDA assumes that predictors are normally distributed (Gaussian distribution) and that the different classes have class-specific means and equal variance/covariance. 
`the equal variance is not true`

Before performing LDA, consider:

-  Inspecting the univariate distributions of each variable and make sure that they are normally distribute. If not, you can transform them using log and root for exponential distributions and Box-Cox for skewed distributions.
-  removing outliers from your data and standardize the variables to make their scale comparable

```{r}
library(MASS)
hresult <- lda(sex~ .,na.action="na.omit", data=hobby)
hresult

# Assess the accuracy of the prediction
# percent correct for each category of G
hresult.values <- predict(hresult)
ct <- table(hobby$sex, hresult.values$class)
diag(prop.table(ct, 1))
# total percent correct
sum(diag(prop.table(ct)))
```


### plot 
```{r}
ldahist(data = hresult.values$x, g=hresult.values$class)
```

```{r load}
# load the data and make each variable right
df1 <- readr::read_csv(file.path(params$output_path, params$csv_fn)) 
```

## Rename variables

We rename some of the variables to make the exposition clearer.

```{r}
df1 <- df1 %>%
  dplyr::rename(., 'motion_dur_thr' = 'med_Motion_duration_Threshold',
                'contrast_thr' = 'med_Contrast_Sensitivity_Threshold',
                'mental_rot' = 'Mental_Rotation_scores',
                'mental_rot_both' = 'Mental_Rotation_scores_both',
                'vocab' = 'Vocabulary_scores',
                'vocab_num' = 'Vocabulary_scores_cor_num')


```

### merge the data 
```{r}
hobbies<-cbind(hobbies,hresult.values$x) 
colnames(hobbies)[2]<-"Participant"
colnames(hobbies)[3]<-"Sex"
colnames(hobbies)[66]<-"Interests"
add<-c(1, 385,"Females", c(rep("NA",64)))
hobbies<-rbind(hobbies, add)
df2<-merge(df1, hobbies[,c(2,3, 66)], by=c("Participant","Sex"))
```

### save the dataframe
```{r}
output_fn <- paste0('combined_', format.Date(Sys.Date()), '.csv')
write.csv(df2,
          file.path(params$output_path, output_fn),
          row.names = FALSE )
```

