---
title: "Code_Clean&visualization"
author: "Yiming Qian"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: hide
params:
  contr_csv_fn: "contrast_output_Oct2020.csv"
  motion_csv_fn: "motion_output_Oct2020.csv"
  qualtrics_csv_fn: "qualtrics_output_10_14_2020.csv"
  this_sub_id: "2019111309492663"
  data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/raw_data"
  output_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  contrast_raw_path: "contrast_sensitivity_task_data"
  motion_raw_path: "motion_temporal_threshold_data"
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
# load the data and make each variable right
cst<-readr::read_csv(file.path(params$output_path,params$contr_csv_fn)) 
cst$Participant<-as.character(cst$Participant)
cst$Gender[1:4]<-0
cst$Gender<-factor(cst$Gender, levels=c(0,"m"), labels=c("Females","Males"))

mdt<-readr::read_csv(file.path(params$output_path,params$motion_csv_fn)) 
mdt$Participant<-as.character(mdt$Participant)
mdt$Gender[313:316]<-0
mdt$Gender<-factor(mdt$Gender, levels=c(0,"m"), labels=c("Females","Males"))

qua_raw<-readr::read_csv(file.path(params$output_path,params$qualtrics_csv_fn)) 
```
rename the participant id
```{r}
# for qualtric survey
qua_raw$participant[which(qua_raw$participant=="2019-11-1309:49:2632")]<-101
qua_raw$participant[which(qua_raw$participant=="2019-11-1311:10:2438")]<-102
qua_raw$participant[which(qua_raw$participant=="2019-11-1313:38:0337")]<-103
qua_raw$participant[which(qua_raw$participant=="2019-11-1314:56:0233")]<-105
qua_raw$participant[which(qua_raw$participant=="2019-11-1316:12:1898")]<-107

qua_raw$participant[which(qua_raw$participant=="2019-11-1808:39:3927")]<-104
qua_raw$participant[which(qua_raw$participant=="2019-11-1811:26:4976")]<-109
qua_raw$participant[which(qua_raw$participant=="2019-11-1812:45:1738")]<-111
qua_raw$participant[which(qua_raw$participant=="2019-11-1813:58:0893")]<-113
qua_raw$participant[which(qua_raw$participant=="2019-11-1814:48:2896")]<-106

qua_raw$participant[which(qua_raw$participant=="2019-11-2013:40:1983")]<-115
qua_raw$participant[which(qua_raw$participant=="2019-11-2014:53:2351")]<-108
qua_raw$participant[which(qua_raw$participant=="2019-11-2016:11:0713")]<-117
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 11:14")]<-119
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 12:17")]<-110

qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 13:54")]<-121
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 10:45")]<-123
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 11:30")]<-125
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 14:35")]<-127
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 16:52")]<-320

qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 17:40")]<-112
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 12:05")]<-114
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 14:36")]<-129
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 16:44")]<-324
qua_raw$participant[which(qua_raw$RecordedDate=="12/5/19 9:59")]<-116

qua_raw$participant[which(qua_raw$RecordedDate=="12/5/19 13:20")]<-131
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 13:23")]<-118
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 14:29")]<-133
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 15:44")]<-120
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 16:44")]<-330

qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 17:45")]<-135
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 13:58")]<-122
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 14:47")]<-124
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 16:32")]<-137
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 17:04")]<-139

# contrast sensitivity
cst$Participant[which(cst$Participant=="2019111309492663")]<-101
cst$Participant[which(cst$Participant=="2019111311102420")]<-102
cst$Participant[which(cst$Participant=="2019111313380357")]<-103
cst$Participant[which(cst$Participant=="201911131456077")]<-105
cst$Participant[which(cst$Participant=="2019111316121877")]<-107

cst$Participant[which(cst$Participant=="20191118083974")]<-104
cst$Participant[which(cst$Participant=="2019111811264955")]<-109
cst$Participant[which(cst$Participant=="2019111812451739")]<-111
cst$Participant[which(cst$Participant=="2.01911e+15")]<-113
# miss one participant here

cst$Participant[which(cst$Participant=="2019112013401963")]<-115
cst$Participant[which(cst$Participant=="2019112014532376")]<-108
cst$Participant[which(cst$Participant=="2019112016110741")]<-117
cst$Participant[which(cst$Participant=="2019112110260325")]<-119
cst$Participant[which(cst$Participant=="2019112111415316")]<-110

cst$Participant[which(cst$Participant=="2019112112563983")]<-121
cst$Participant[which(cst$Participant=="2019112209583295")]<-123
cst$Participant[which(cst$Participant=="2019112210523539")]<-125
cst$Participant[which(cst$Participant=="2019112213492145")]<-127
cst$Participant[which(cst$Participant=="201911221604385")]<-320 

cst$Participant[which(cst$Participant=="2019112217002412")]<-112
cst$Participant[which(cst$Participant=="2019120409523578")]<-114
cst$Participant[which(cst$Participant=="2019120413585457")]<-129
cst$Participant[which(cst$Participant=="201912041554552")]<-324
cst$Participant[which(cst$Participant=="2019120509244570")]<-116

cst$Participant[which(cst$Participant=="2019120512235593")]<-131
cst$Participant[which(cst$Participant=="20191212114750")]<-118
cst$Participant[which(cst$Participant=="2019121212434199")]<-133
cst$Participant[which(cst$Participant=="2019121214503690")]<-120
cst$Participant[which(cst$Participant=="2019121215561995")]<-330

cst$Participant[which(cst$Participant=="2019121217013332")]<-135
cst$Participant[which(cst$Participant=="2019121313154134")]<-122
cst$Participant[which(cst$Participant=="2019121314001724")]<-124
cst$Participant[which(cst$Participant=="2019121315012099")]<-137
cst$Participant[which(cst$Participant=="2019121316322025")]<-139
# 131 participants

# motion duration
mdt$Participant[which(mdt$Participant=="2019111309492663")]<-101
mdt$Participant[which(mdt$Participant=="2019111311102420")]<-102
mdt$Participant[which(mdt$Participant=="2019111313380357")]<-103
mdt$Participant[which(mdt$Participant=="2019111314560277")]<-105 # differnt from cst
mdt$Participant[which(mdt$Participant=="2019111316121877")]<-107

mdt$Participant[which(mdt$Participant=="20191118083974")]<-104
mdt$Participant[which(mdt$Participant=="2019111811264955")]<-109
mdt$Participant[which(mdt$Participant=="2019111812451739")]<-111
mdt$Participant[which(mdt$Participant=="2019111813580899")]<-113 # differnt from cst
mdt$Participant[which(mdt$Participant=="2019111814482814")]<-106

mdt$Participant[which(mdt$Participant=="2019112013401963")]<-115
mdt$Participant[which(mdt$Participant=="2019112014532376")]<-108
mdt$Participant[which(mdt$Participant=="2019112016110741")]<-117
mdt$Participant[which(mdt$Participant=="2019112110260325")]<-119
mdt$Participant[which(mdt$Participant=="2019112111415316")]<-110

mdt$Participant[which(mdt$Participant=="2019112112563983")]<-121
mdt$Participant[which(mdt$Participant=="2019112209583295")]<-123
mdt$Participant[which(mdt$Participant=="2019112210523539")]<-125
mdt$Participant[which(mdt$Participant=="2019112213492145")]<-127
mdt$Participant[which(mdt$Participant=="201911221604385")]<-320 

mdt$Participant[which(mdt$Participant=="2019112217002412")]<-112
mdt$Participant[which(mdt$Participant=="2019120409523578")]<-114
mdt$Participant[which(mdt$Participant=="2019120413585457")]<-129
mdt$Participant[which(mdt$Participant=="201912041554552")]<-324
mdt$Participant[which(mdt$Participant=="2019120509244570")]<-116

mdt$Participant[which(mdt$Participant=="2019120512235593")]<-131
mdt$Participant[which(mdt$Participant=="20191212114750")]<-118
mdt$Participant[which(mdt$Participant=="2019121212434199")]<-133
mdt$Participant[which(mdt$Participant=="2019121214503690")]<-120
mdt$Participant[which(mdt$Participant=="2019121215561995")]<-330

mdt$Participant[which(mdt$Participant=="201912121703332")]<-135   # differnt from cst
mdt$Participant[which(mdt$Participant=="2019121313154134")]<-122
mdt$Participant[which(mdt$Participant=="2019121314001724")]<-124
mdt$Participant[which(mdt$Participant=="2019121315012099")]<-137
mdt$Participant[which(mdt$Participant=="2019121316322025")]<-139 # missed
# miss 371, half of 395

# it should be 132 participants
```

Delete the test participants in qualtrics
```{r}
qua_raw$participant<-as.numeric(qua_raw$participant)

qua<-qua_raw[,-c(1:6, 8:17)] %>%
  filter(Finished==1) %>%
  filter(participant!="test") %>%
  filter(participant!=0) 

length(unique(qua$participant))
# miss one 385
```

# delete the items with 99 
```{r}
which( qua ==99, arr.ind=T )
which( qua[,161:220] ==99, arr.ind=T )
which( qua[,161:220] ==98, arr.ind=T )
which( qua[,161:220] ==88, arr.ind=T )
which( qua$Flag_MRT ==1, arr.ind=T ) # Flag individuals with more than 40 responses (i.e., who did not follow directions).# 3 participants

# replace 99 with NA
qua[,161:220] <- na_if(qua[,161:220], 99)
```
# calculate hobby_mean and m/f hobby
```{r}
hobby_temp<-qua[,c(161:220)] 
qua$hobby_mean<-rowMeans(hobby_temp,na.rm=T)
qua$fem<-rowMeans(hobby_temp[,c(3,8,9,10,14,15,19,20,21,37,43,45,50,53,54,55,56,59,60)],na.rm=T)
qua$mas<-rowMeans(hobby_temp[,c(1,6,11,17,18,22,23,24,25,28,31,33,34,35,39,41,42,44,48,57,58)],na.rm=T)
qua$femscale<-qua$fem-qua$hobby_mean
qua$masscale<-qua$mas-qua$hobby_mean
```

# calculate alpha
```{r}
feshob<-data.frame(hobby_temp[,c(3,8,9,10,14,15,19,20,21,37,43,45,50,53,54,55,56,59,60)])
psych::alpha(feshob)
mashob<-data.frame(hobby_temp[,c(1,6,11,17,18,22,23,24,25,28,31,33,34,35,39,41,42,44,48,57,58)])
psych::alpha(mashob)
```
> We will exclude final scores of spatial ability, hobbies, and verbal ability data which are zero.

```{r}
which(qua$advoc_num_cor==0)
which(qua$MRT_cor==0)
which(qua$fem==0)
which(qua$mas==0)

which(qua$advoc_num_cor>36)
which(qua$MRT_cor>40)
which(qua$fem>5)
which(qua$mas>5)
```
> We will exclude the run of visual perception tasks with less than 50% accuracy (guess rate).

The marginal error is 1.97*sqrt(p(1-p)/30)=0.18
The 95 confidence intervals are 50% +/- 18% [32% 68%]
We will exclude the runs with less than 68% accuracy.
```{r}
which(cst$percent_correct<0.68)  # 29  30  31  32 371
which(mdt$percent_correct<0.68) # 85  86  87  88 325 326 327 328 480 504 505
cst$Participant[which(cst$percent_correct<0.68)] # "111" "111" "111" "111" "393"
mdt$Participant[which(mdt$percent_correct<0.68)] # "114" "114" "114" "114" "383" "383" "383" "383" "422" "428" "428"
cst<-cst %>% filter(percent_correct>=0.68)
mdt<-mdt %>% filter(percent_correct>=0.68)
```


Visualization
```{r}
# visualization
hist(cst$threshold)
boxplot(cst$threshold)
str(cst)

hist(mdt$threshold)
boxplot(mdt$threshold)
str(mdt)
```

```{r}
# visualization-cst
cst %>% ggplot(aes(x=threshold,group=run, color=run)) +
  geom_density() + 
  facet_grid(~Gender)

cst %>% ggplot(aes(x=threshold,group=Gender, color=Gender)) +
  geom_density() 

psych::describe(cst)
psych::describeBy(cst,group=cst$Gender)
cst %>%
  group_by(Gender) %>%
  summarize(mean=mean(threshold),
            sd=sd(threshold),
            median=median(threshold),
            count=n())
```

```{r}
# visualization-mdt
na.omit(mdt) %>% ggplot(aes(x=threshold,group=run, color=run)) +
  geom_density() + 
  facet_grid(~Gender)

na.omit(mdt) %>% ggplot(aes(x=threshold,group=Gender, color=Gender)) +
  geom_density() 

psych::describe(cst)
psych::describeBy(cst,group=cst$Gender)
mdt %>%
  group_by(Gender) %>%
  summarize(mean=mean(threshold),
            sd=sd(threshold),
            median=median(threshold),
            count=n())
```


Clean the threshold which clearly have something wrong by each cumulative figures
```{r}
# check the cumulative figures of contrast sensitivity for each participant (up tp 366)
# 2019111811264955, 2019112210523539, 2019112217002412,20191205244570, 338, 339, 342, 344, 347, 351, 352, 358, 365, 366, 372, 375, 385, 388, 391, 402, 404, 410, 413, 416, 420, 421, 428 has one run very different from the others
# 350, 379, 431 has two runs very different from the others
# 393 (the 3rd, deleted due to low accuracy),417 (none is deleted) has a weird run
# 2019111812451739 (all deleted) has 4 wrong runs
cst$threshold[which(cst$threshold>1)]

# check the cumulative figures of contrast sensitivity for each participant (up tp 366)
# 2019111811264955, 2019111814482814, 2019112217002412, 2019121313154134, 338, 349, 350, 374, 376, 404,405 has one run very different from the others
# 2019112213492145, 393 has two runs very different from the others
# 20191119083974 (this may be a test data), 2019121215561995 (330,none is deleted), 354 (none is deleted) , 422 (the 1st, deleted due to low accuracy) has 1 weird runs
# 201912040923578 (all deleted), 383 (all deleted), 428 (2 runs deleted due to low accuracy), 431 (none is deleted) has 4 wrong runs
mdt$threshold[which(mdt$threshold>0.30)]
mdt$Participant[which(mdt$threshold>0.30)]
```

get median
```{r}
cst_median <- cst %>%
  group_by(Participant, Gender) %>%
  summarise(cst_median = median(threshold),
            cst_mean = mean(threshold),
            cst_sd = sqrt(var(threshold)))

mdt_median <- mdt %>%
  group_by(Participant, Gender) %>%
  summarise(mdt_median = median(threshold),
            mdt_mean = mean(threshold),
            mdt_sd = sqrt(var(threshold)))
```

merge dataframes
```{r}
qua$sex<-factor(qua$sex, levels=c(2,1), labels=c("Females","Males"))
names(qua)[names(qua)=="sex"] <- "Gender"
names(qua)[names(qua)=="participant"] <- "Participant"
qua$Participant<-as.character(qua$Participant)
df <- full_join(mdt_median,cst_median, by=c("Participant","Gender")) %>% # 128 and 130 rows->132
  full_join(qua,k, by=c("Participant","Gender"))  # 131, 132 rows->132 rows?
```
check visual acuity outliers
>We will exclude the participant whose visual acuity is equal to or worse than 20/40 in HOTV visual acuity chart.

```{r}
# no participant with visual acuity lower than 20/40.
```

add other variables
```{r}
df$race <- ""
df$colorvision <- NA
df$race_5 <- as.numeric(df$race_5)
# df$race_sum<-rowSums(df[,10:16],na.rm=TRUE)
#df$race_sum <- rowSums(df[, 'race_1':'race_7'], na.rm = TRUE)
#df$race_sum[which(df$race_sum != 1)]
df$race[which(df$race_1 == 1)] <- "Asian"
df$race[which(df$race_2 == 1)] <-
  paste(df$race, "Black/African", sep = ",")
df$race[which(df$race_3 == 1)] <- paste(df$race, "Caucasian", sep = ",")
df$race[which(df$race_4 == 1)] <-
  paste(df$race, "Hispanic/Latino", sep = ",")
df$race[which(df$race_5 == 1)] <-
  paste(df$race, "Native American", sep = ",")
df$race[which(df$race_6 == 1)] <-
  paste(df$race, "Pacific Islander", sep = ",")
df$race[which(df$race_7 == 1)] <-
  paste(df$race, "Prefer not to answer", sep = ",")
# df$race[which(df$race_sum==2)]<-"Multiple"
which(df$color_vision1_4 != 1)
which(df$color_vision1_5 != 1)
which(df$color_vision2_1 != 4)
which(df$color_vision2_2 != 4) #4   9  11  64  73  92  95 102 129
which(df$color_vision2_3 != 4)  #92
#df$colorvision <- rowSums(df[, 226:228], na.rm = TRUE)
#df$colorvision <- rowSums(df[, 'color_vision1_4':'color_vision_2_3'], na.rm = TRUE)
```



```{r}
# save data
var <-
  c(
    "Participant",
    "Gender",
    "race",
    "age",
    "schoolyear",
    "major",
    "handedness",
    "glasses",
    "acuity",
    "colorvision",
    "stereo",
    "mdt_median",
    "mdt_mean",
    "mdt_sd",
    "cst_median",
    "cst_mean",
    "cst_sd",
    "advoc_total_score",
    "advoc_num_cor",
    "MRT_cor",
    "MRT_cor_both",
    "fem",
    "mas",
    "hobby_mean",
    "femscale",
    "masscale"
  )
df1 <- df[, var]
colnames(df1) <-
  c(
    "Participant",
    "Sex",
    "Race",
    "Age",
    "School_year",
    "Major",
    "Handedness",
    "Glasses",
    "Acuity",
    "Color_vision",
    "Stereo",
    "motion_dur_thr",
    "motion_dur_thr_mean",
    "motion_dur_thr_sd",
    "contrast_thr",
    "contrast_thr_mean",
    "contrast_thr_sd",
    "vocab",
    "Vocabulary_scores_cor_num",
    "mental_rot",
    "Mental_Rotation_scores_both",
    "Feminine_hobbies",
    "Masculine_hobbies",
    "hobby_mean",
    "femscale",
    "masscale"
  )
# write.csv(df1,
#           file.path(params$output_path, "data_output_Oct2020.csv"),
#           row.names = FALSE)
df1$mf<-df1$masscale-df1$femscale
output_fn <- paste0('combined_', format.Date(Sys.Date()), '.csv')
write.csv(df1,
          file.path(params$output_path, output_fn),
          row.names = FALSE)
```




