---
title: "Gather, Clean, & Plot Both Tasks"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: hide

params:
  this_contr_csv_fn: "~/Box\ Sync/Project_Sex_difference_on_Motion_Perception/data/raw_data/contrast_sensitivity_task_data/2019111309492663_contrast_sensitivity_task.csv"
  this_motion_dur_csv_fn: "~/Box\ Sync/Project_Sex_difference_on_Motion_Perception/data/raw_data/motion_temporal_threshold_data/2019111309492663_motion_temporal_threshold.csv"
  this_sub_id: "2019111309492663"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
```

# Report for `r params$this_sub_id`

## Purpose

This script imports, summarizes, and shows basic visualizations of an individual's session data.


## Contrast sensitivity task

### Import

```{r}
s_data <- readr::read_csv(params$this_contr_csv_fn)
```

#### File-level checks

At least 130 trials?

```{r n-trials}
n_trials <- dim(s_data)[1]
```

File has $n=$ `r n_trials` rows.

Are all of the critical fields in the file?

```{r}
essential_fields <- c("correctAns", "loop_trial.intensity", "loop_trial.thisN",
                      "Participant", "Gender", "resp.rt")

all_fields <- essential_fields %in% names(s_data)
```

Of the `r length(essential_fields)`, `r sum(all_fields)` are in the file.

Is the gender variable specified?

```{r}
gender_specified <- !(is.na(s_data$Gender))
```


#### Clean and rename variables

```{r import-contrast-sens}
s1_clean <- s_data %>%
  mutate(., correctAns = stringr::str_extract(correctAns, "left|down|right|up")) %>%
  mutate(., corr = if_else(resp == correctAns, 1, 0)) %>%
  rename(., contr = loop_trial.intensity,
         trial_n = loop_trial.thisN)

s1_subset <- s1_clean %>%
  dplyr::select(., Participant, Gender,
                trial_n,
                contr,
                correctAns,
                resp,
                corr,
                resp.rt) %>%
  dplyr::filter(., trial_n >= 0) %>%
  dplyr::mutate(run = rep(1:4, each=30))
```

### Visualize

```{r contrast-sensitivity-by-trial}
s1_subset %>% ggplot(.) +
  aes(x = trial_n, y = contr) +
  facet_grid(. ~ run) +
  geom_smooth() +
  geom_point() +
  ggtitle("Contrast sensitivity data")
```

#### Cumulative performance across runs

```{r contrast-sensitivity-cum-p}
s1_subset <- s1_subset %>%
  dplyr::group_by(., run) %>%
  dplyr::arrange(., contr) %>%
  dplyr::mutate(., cum_sum = cumsum(corr),
                cum_p = cum_sum/n())

s1_subset %>% ggplot(.) +
  aes(x = contr, y = cum_p) +
  facet_grid(. ~ run) +
  geom_point() +
  geom_smooth(se = FALSE) +
  ggtitle("Contrast sensitivity data")
```

#### RT

```{r contrast-sensitivity-rt}
s1_subset %>%
  ggplot(.) +
  aes(x = trial_n, y = resp.rt) +
  facet_grid(. ~ run) + 
  geom_point() +
  ggtitle("Contrast sensitivity data")
```


## Motion duration task

### Import

```{r}
md_data <- readr::read_csv(params$this_motion_dur_csv_fn)
```

```{r}
md_clean <- md_data %>%
  mutate(., run = run_n + 1) %>%
  rename(., corr = correct,
         dur_s = FWHM)

md_subset <- md_clean %>%
  dplyr::select(.,
                run,
                trial_n,
                dur_s,
                corr,
                rt)
```

### Visualize

```{r motion-temporal-threshold-by-trial}
md_subset %>% ggplot(.) +
  aes(x = trial_n, y = dur_s) +
  facet_grid(. ~ run) +
  geom_smooth() +
  geom_point() +
  ggtitle("Motion temporal duration threshold data")
```

#### Cumulative performance across runs

```{r motion-temporal-threshold-rt-cum-p}
md_subset <- md_subset %>%
  dplyr::group_by(., run) %>%
  dplyr::arrange(., dur_s) %>%
  dplyr::mutate(., cum_sum = cumsum(corr),
                cum_p = cum_sum/n())

md_subset %>% ggplot(.) +
  aes(x = dur_s, y = cum_p) +
  facet_grid(. ~ run) +
  geom_point() +
  geom_smooth(se = FALSE)  +
  ggtitle("Motion temporal duration threshold data")
```

#### RT

```{r motion-temporal-threshold-rt}
md_subset %>%
  ggplot(.) +
  aes(x = trial_n, y = rt) +
  facet_grid(. ~ run) + 
  geom_point()  +
  ggtitle("Motion temporal duration threshold data")
```
