---
title: "Gather & Clean Qualtrics Surveys"
subtitle: "Sex Differences Project"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
params:
  box_path: "~/Box Sync"
  data_path: "/Project_Sex_difference_on_Motion_Perception/data"
  qualtrics_raw_path: "/raw_data/qualtrics_survey_data/csv"
  old_survey_fn: "survey_REV_2019-11-11.csv"
  new_survey_fn: "survey_REV_2019-11-18.csv"
  update_raw: true
  reimport_raw: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(qualtRics)
```

# Purpose

This document describes the process of gathering and cleaning the Qualtrics survey data for the sex differences project.

To render, enter `rmarkdown::render("analysis/gather-clean-qualtrics.Rmd", params = list(box_path = "<YOUR_BOX_PATH>"))`, substituting the path to your Box folder on your local machine.
On Mac OS the default is "~/Box Sync".

# Background

## Connecting to Qualtrics via the API

I used `qualtRics::qualtrics_api_credentials()` to install the credentials per the instructions here: <https://github.com/ropensci/qualtRics>.
Note that this writes credentials data to the user's R Environment (`.Renviron`) variable.
This file should **not** be synched to GitHub for security reasons.
The default `.gitignore` for the repository includes an entry that excludes `.Renviron` from git version control.

## Qualtrics survey(s)

Our survey data comes from two different "published" surveys:
  - "Sex difference survey REV 2019-11-11"
  - "Sex difference survey REV 2019-11-18"
  
This script imports both.

# Gather data from Qualtrics

```{r import-from-qualtrics}
old_active_survey_name <- "Sex difference survey REV 2019-11-11"
active_survey_name <- "Sex difference survey REV 2019-11-18"

surveys <- qualtRics::all_surveys()

active_survey <- surveys %>%
  filter(., name == active_survey_name)

old_active_survey <- surveys %>%
  filter(., name == old_active_survey_name)

sex_diff_resp <- qualtRics::fetch_survey(surveyID = active_survey$id,
                                     verbose = TRUE,
                                     force_request = TRUE)
sex_diff_quest <- qualtRics::survey_questions(surveyID = active_survey$id)
sex_diff_meta <- qualtRics::metadata(surveyID = active_survey$id)

# Get data from prior to 2019-11-18
old_sex_diff_resp <- qualtRics::fetch_survey(surveyID = old_active_survey$id,
                                             verbose = TRUE,
                                     force_request = TRUE)
old_sex_diff_quest <- qualtRics::survey_questions(surveyID = old_active_survey$id)
old_sex_diff_meta <- qualtRics::metadata(surveyID = old_active_survey$id)
```

There are `r sex_diff_meta$responsecounts$auditable` surveys from the current active survey, and `r old_sex_diff_meta$responsecounts$auditable` from the older inactive survey.

## Active survey

```{r show-newer-survey}
# In "Sex difference survey REV 2019-11-18", Q97 contains the participant ID
sex_diff_resp %>%
  dplyr::select(., StartDate, `Q97`, `Q1`) %>%
  dplyr::rename(., p_id = `Q97`, 
                gender = `Q1`) %>%
  knitr::kable(.) %>%
  kableExtra::kable_styling("hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

## Older survey

```{r show-older-survey}
# In "Sex difference survey REV 2019-11-18", Q97 contains the participant ID
old_sex_diff_resp %>%
  dplyr::select(., StartDate, `Participant ID`, `Q1`) %>%
  dplyr::rename(., p_id = `Participant ID`,
                gender = `Q1`) %>%
  knitr::kable(.) %>%
  kableExtra::kable_styling("hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

## Export

```{r, export-to-raw}
if (params$update_raw) {
  # Create directory if needed
  qualtrics_raw_dir <- paste0(params$box_path, params$data_path,
                   params$qualtrics_raw_path)
  if (!dir.exists(qualtrics_raw_dir)) {
    message(paste0("Creating new directory ", qualtrics_raw_dir))
    dir.create(qualtrics_raw_dir)
  }
  
  # Old survey data
  old_fn <- paste0(params$box_path, params$data_path,
                   params$qualtrics_raw_path, "/", params$old_survey_fn)
  if (file.exists(old_fn)) {
    message("Raw survey file exists. Overwriting.")
  } else {
    message("Creating new raw survey file.")
  }
  readr::write_csv(old_sex_diff_resp, old_fn)
  
  # New survey data
  new_fn <- paste0(params$box_path, params$data_path,
                   params$qualtrics_raw_path, "/", params$new_survey_fn)
  if (file.exists(new_fn)) {
    message("Raw survey file exists. Overwriting.")
  } else {
    message("Creating new raw survey file.")
  }
  readr::write_csv(sex_diff_resp, new_fn)  
} else {
  message("Qualtrics raw data not exported.")
}
```

# Data cleaning

## Reimport raw

If `params$reimport_raw == TRUE` (the default), we reimport the exported raw files to make sure that our pipeline is robust.

```{r}
if (params$reimport_raw) {
  message("Reimporting previously saved raw Qualtrics survey files.")
  qualtrics_csvs <- list.files(path = qualtrics_raw_dir, 
                               pattern = "\\.csv", full.names = TRUE)
  
  old_survey_index <- stringr::str_detect(qualtrics_csvs, params$old_survey_fn)
  new_survey_index <- stringr::str_detect(qualtrics_csvs, params$new_survey_fn)
  
  old_survey_full_fn <- qualtrics_csvs[old_survey_index]
  new_survey_full_fn <- qualtrics_csvs[new_survey_index]
  
  sex_diff_resp <- readr::read_csv(new_survey_full_fn)
  old_sex_diff_resp <- readr::read_csv(old_survey_full_fn)  
}
```

## Active survey

Several of the nominal variables are spread into separate columns, e.g., `Q89` gets split into multiple ethnicity categories.

```{r clean-newer-survey}
sex_diff_demo <- sex_diff_resp %>%
  dplyr::rename(., p_id = `Q97`) %>%
  tidyr::gather(., key="quest", 
                value="ethnicity", Q89_1, Q89_2, Q89_3, Q89_4, 
                Q89_5, Q89_6, Q89_7) %>%
  dplyr::filter(., !is.na(ethnicity)) %>%
  dplyr::select(., -quest) %>%
  dplyr::mutate(., p_id = stringr::str_remove_all(p_id, "[:-]")) %>%
  dplyr::rename(., vis_acuity = `Q81`) %>%
  dplyr::rename(., gender = `Q1`) %>%
  dplyr::rename(., age_yrs = `Q4`) %>%
  dplyr::rename(., school_yr = `Q2`) %>%
  dplyr::rename(., major = `Q3`) %>%
  dplyr::rename(., preferred_hand = `Q88`) %>%
  dplyr::rename(., stereo_vision = `Q92`) %>%
  dplyr::rename(., test_date = StartDate) %>%
  dplyr::rename(., expt_notes = `Q99`) %>%
  dplyr::select(., test_date, p_id, gender, age_yrs, school_yr, major,
                preferred_hand, vis_acuity, stereo_vision, expt_notes) %>%
  dplyr::arrange(., test_date)
```

```{r summarize-demo-newer-survey}
xtabs(~ gender + age_yrs, data = sex_diff_demo) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

## Older survey

```{r clean-old-survey}
old_sex_diff_demo <- old_sex_diff_resp %>%
  dplyr::rename(., p_id = `Participant ID`) %>%
  tidyr::gather(., key="quest", 
                value="ethnicity", Q89_1, Q89_2, Q89_3, Q89_4, 
                Q89_5, Q89_6, Q89_7) %>%
  dplyr::filter(., !is.na(ethnicity)) %>%
  dplyr::select(., -quest) %>%
  dplyr::mutate(., p_id = stringr::str_remove_all(p_id, "[:-]")) %>%
  dplyr::rename(., vis_acuity = `Q81`) %>%
  dplyr::rename(., gender = `Q1`) %>%
  dplyr::rename(., age_yrs = `Q4`) %>%
  dplyr::rename(., school_yr = `Q2`) %>%
  dplyr::rename(., major = `Q3`) %>%
  dplyr::rename(., preferred_hand = `Q88`) %>%
  dplyr::rename(., stereo_vision = `Q92`) %>%
  dplyr::rename(., test_date = StartDate) %>%
  dplyr::mutate(., expt_notes = NA) %>%
  dplyr::select(., test_date, p_id, gender, age_yrs,
                school_yr, major,
                preferred_hand, vis_acuity, stereo_vision, expt_notes) %>%
  dplyr::arrange(., test_date)
```

```{r summarize-demo-older-survey}
xtabs(~ gender + age_yrs, data = old_sex_diff_demo) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") 
```

## Combined

```{r, echo=FALSE}
combined_demo <- rbind(old_sex_diff_demo, sex_diff_demo)
combined_demo_gender_only <- combined_demo %>%
  dplyr::group_by(., gender) %>%
  dplyr::select(., gender)

xtabs(~ gender, data = combined_demo_gender_only) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") 
```

# Data merging

The merged dataset can be used to address duplicate entries and to conduct quality assurance (QA) checks.

```{r}
merged_demo <- rbind(sex_diff_demo, old_sex_diff_demo)
merged_demo <- merged_demo %>%
  dplyr::arrange(., test_date)

merged_demo %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```

# Quality Assurance (QA) checks

First, we define the criteria each survey must meet to pass this level of QA.
Each criterion is defined as a Boolean function.

The `vis_acuity` and `stereo_vision` variables are optional.

```{r qa-check-functions}
observer_id_in_file <- function(data_df) {
  !is.na(data_df$p_id)
}

gender_in_file <- function(data_df) {
  !is.na(data_df$gender) 
}

gender_male_or_female <- function(data_df) {
  data_df$gender %in% c("Female", "Male")
}

age_yrs_valid <- function(data_df) {
  !is.na(data_df$age_yrs) & (data_df$age_yrs %in% c("18-19", "20-21",
                                                        "22-23",
                                                        "older than 23"))
}

school_yr_valid <- function(data_df) {
  !is.na(data_df$school_yr) & (data_df$school_yr %in% c("Freshman", 
                                                        "Sophomore",
                                                        "Junior", 
                                                        "Senior", 
                                                        "5th year or later"))
}

preferred_hand_valid <- function(data_df) {
  !is.na(data_df$preferred_hand) & (data_df$preferred_hand %in% c("Left hand", 
                                                        "Right hand",
                                                        "Either hand"))
}

poss_exclude <- function(data_df) {
  out <- rep(FALSE, dim(data_df)[1])
  
  # questionable p_id
  bad_p_id <- data_df$p_id %in% c("000", "test", 
                                  "0000", "00000")
  out[bad_p_id] <- TRUE
  
  # other exclusion reasons...
  
  # pilot participants
  
  out
}
```

```{r qa-table}
merged_demo <- merged_demo %>%
  dplyr::mutate(., observer_id_in_file = observer_id_in_file(merged_demo),
                gender_in_file = gender_in_file(merged_demo),
                gender_male_or_female = gender_male_or_female(merged_demo),
                age_yrs_valid = age_yrs_valid(merged_demo),
                school_yr_valid = school_yr_valid(merged_demo),
                preferred_hand_valid = preferred_hand_valid(merged_demo),
                poss_exclude = poss_exclude(merged_demo))

merged_demo %>%
  select(., test_date, expt_notes, p_id, poss_exclude,
         observer_id_in_file,
         gender_in_file,
         gender_male_or_female,
         age_yrs_valid,
         school_yr_valid,
         preferred_hand_valid) %>%
  knitr::kable(., 'html') %>%
  kableExtra::kable_styling(., "hover", "striped") %>%
  kableExtra::scroll_box(., height = "300px")
```
