---
title: "Hobbies"
author: "Yiming Qian & Rick Gilmore"
date: "`r Sys.time()`"
css: report.css
output: 
  html_document:
    self_contained: yes
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
params:
  data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  csv_fn: "qualtrics_output_10_14_2020.csv"
---

# Purpose

This document describes analyses and visualizations of the hobby-choices data from the sex differences in vision project.

# Setup

This section loads the R packages needed to support the following sections.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

# Source packages
library(tidyverse)
library(parameters)
library(sjPlot)
library(expss)
library(pwr)
library(ggpubr)
library(parameters)
```

# Import and clean

The hobbies data are embedded in a much larger Qualtrics data file.

```{r load}
data_fn <- file.path(file.path(params$data_path, params$csv_fn))
if (!file.exists(data_fn)) {
  stop('Data file cannot be found: `', data_fn, '`.')
}
surveys_df <- readr::read_csv(data_fn)
```

Let's look at the data using the `str()` or 'structure' function.

```{r}
str(surveys_df)
```

We need to work with Yiming to determine what rows to select.
For now, let's keep `sex`, `age`, `schoolyear`, `major`, `race_1`:`race_7`, `handedness`,  the hobbies questions `h1`:`h60`, `acuity`, `color_vision1_4`:`color_vision_2_3`, `stereo`, and `hobfem` and `hobmas`.

```{r}
hobbies_df <- surveys_df %>%
  dplyr::select(., 
                StartDate,
                participant,
                sex,
                age,
                schoolyear,
                major,
                race_1:race_7,
                handedness,
                h1:h60,
                acuity,
                color_vision1_4:color_vision2_3,
                stereo,
                hobfem,
                hobmas
                )

str(hobbies_df)
```

## Clean

We'll need to clean the `major` variable, the `race_` variables, the `color_vision` variables, rename the hobby variables to reflect the actual hobby asked about, and we'll also want to label the hobbies as male- or female-typed.

## Export cleaned file for use on RStudio Server Pro

To facilitate students' use of RStudio Server Pro, here is code to export this trimmed dataset.

```{r}
readr::write_csv(hobbies_df, 'csv/hobbies_sex_diff.csv')
```



