---
title: "Import, clean, and export data"
author: "Yiming Qian & Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: yes
    code_folding: show
    toc: yes
    toc_depth: 3
params:
  contr_csv_fn: "contrast_output_Oct2020.csv"
  motion_csv_fn: "motion_output_Oct2020.csv"
  qualtrics_csv_fn: "qualtrics_output_10_14_2020.csv"
  hobbies_csv_fn: "sexdiff_data.csv"
  processed_data_path: "~/OneDrive - The Pennsylvania State University/Box Migration Data/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  output_path: "csv"
---

# Purpose

This document shows the steps involved in importing and cleaning the study data.

The document imports the raw (by-participant) data for the contrast threshold task, the motion duration threshold task, and associated Qualtrics data. It cleans the data, merges it, and exports a combined data file.

# Set-up

We use the `tidyverse` package.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Import data

## Contrast sensitivity task

These data include a maximum of four runs for each participant.

```{r, import-contrast}
# load the data and make each variable right
cst <-
  readr::read_csv(file.path(params$processed_data_path, params$contr_csv_fn))
```

The structure of the data are as follows:

```{r}
str(cst)
```

`Participant`: unique identifier for each participant. The initial participants had a date/timestamp. Later ones had an integer.

`Gender`: Self-reported sex. Values in `{0, 'm'}`

`run`: Integer indicating which of 4 runs of the task are indicated by the data.

`shape`: Weibull function shape parameter.

`scale`: Weibull function scale parameter.

`loglik`: Loglikelihood value for the best-fitting Weibull function.

`threshold`: Constrast sensitivity threshold estimate (in proportion of contrast) based on the best-fitting Weibull function.

`percent_correct`: Percent correct judgments within a run.

The dimensions of the data are as follows:

```{r}
dim(cst)
```

### Motion duration threshold task

These data include a maximum of four runs for each participant.

```{r, import-motion}
mdt <-
  readr::read_csv(file.path(params$processed_data_path, params$motion_csv_fn))
```

The structure of the data are as follows:

```{r}
str(mdt)
```

`Participant`: unique identifier for each participant. The initial participants had a date/timestamp. Later ones had an integer.

`Gender`: Self-reported sex. Values in `{0, 'm'}`

`run`: Integer indicating which of 4 runs of the task are indicated by the data.

`shape`: Weibull function shape parameter.

`scale`: Weibull function scale parameter.

`loglik`: Loglikelihood value for the best-fitting Weibull function.

`threshold`: Motion duration threshold estimate (in secs) based on the best-fitting Weibull function.

`percent_correct`: Percent correct judgments within a run.

The dimensions of the data are as follows:

```{r}
dim(mdt)
```

### Qualtrics data

```{r, import-qualtrics}
qua_raw <-
  readr::read_csv(file.path(params$processed_data_path, params$qualtrics_csv_fn)) 
```

# Clean data

## Participant identifiers

### Contrast sensitivity

```{r}
# Make Participant character
cst$Participant <- as.character(cst$Participant)
```

Convert date-time stamps to integers.

```{r}
cst$Participant[which(cst$Participant == "2019111309492663")] <- 101
cst$Participant[which(cst$Participant == "2019111311102420")] <- 102
cst$Participant[which(cst$Participant == "2019111313380357")] <- 103
cst$Participant[which(cst$Participant == "201911131456077")] <- 105
cst$Participant[which(cst$Participant == "2019111316121877")] <- 107

cst$Participant[which(cst$Participant == "20191118083974")] <- 104
cst$Participant[which(cst$Participant == "2019111811264955")] <- 109
cst$Participant[which(cst$Participant == "2019111812451739")] <- 111
cst$Participant[which(cst$Participant == "2.01911e+15")] <- 113

# missing one participant here?

cst$Participant[which(cst$Participant == "2019112013401963")] <- 115
cst$Participant[which(cst$Participant == "2019112014532376")] <- 108
cst$Participant[which(cst$Participant == "2019112016110741")] <- 117
cst$Participant[which(cst$Participant == "2019112110260325")] <- 119
cst$Participant[which(cst$Participant == "2019112111415316")] <- 110

cst$Participant[which(cst$Participant == "2019112112563983")] <- 121
cst$Participant[which(cst$Participant == "2019112209583295")] <- 123
cst$Participant[which(cst$Participant == "2019112210523539")] <- 125
cst$Participant[which(cst$Participant == "2019112213492145")] <- 127
cst$Participant[which(cst$Participant == "201911221604385")] <- 320

cst$Participant[which(cst$Participant == "2019112217002412")] <- 112
cst$Participant[which(cst$Participant == "2019120409523578")] <- 114
cst$Participant[which(cst$Participant == "2019120413585457")] <- 129
cst$Participant[which(cst$Participant == "201912041554552")] <- 324
cst$Participant[which(cst$Participant == "2019120509244570")] <- 116

cst$Participant[which(cst$Participant == "2019120512235593")] <- 131
cst$Participant[which(cst$Participant == "20191212114750")] <- 118
cst$Participant[which(cst$Participant == "2019121212434199")] <- 133
cst$Participant[which(cst$Participant == "2019121214503690")] <- 120
cst$Participant[which(cst$Participant == "2019121215561995")] <- 330

cst$Participant[which(cst$Participant == "2019121217013332")] <- 135
cst$Participant[which(cst$Participant == "2019121313154134")] <- 122
cst$Participant[which(cst$Participant == "2019121314001724")] <- 124
cst$Participant[which(cst$Participant == "2019121315012099")] <- 137
cst$Participant[which(cst$Participant == "2019121316322025")] <- 139
```

The number of unique participants is as follows:

```{r}
length(unique(cst$Participant))
```

### Motion duration

```{r}
# Make Participant character
mdt$Participant <- as.character(mdt$Participant)
```

Convert date-time stamps to integers.

```{r}
mdt$Participant[which(mdt$Participant == "2019111309492663")] <- 101
mdt$Participant[which(mdt$Participant == "2019111311102420")] <- 102
mdt$Participant[which(mdt$Participant == "2019111313380357")] <- 103
mdt$Participant[which(mdt$Participant == "2019111314560277")] <-
  105 # different from cst?
mdt$Participant[which(mdt$Participant == "2019111316121877")] <- 107

mdt$Participant[which(mdt$Participant == "20191118083974")] <- 104
mdt$Participant[which(mdt$Participant == "2019111811264955")] <- 109
mdt$Participant[which(mdt$Participant == "2019111812451739")] <- 111
mdt$Participant[which(mdt$Participant == "2019111813580899")] <-
  113 # different from cst
mdt$Participant[which(mdt$Participant == "2019111814482814")] <- 106

mdt$Participant[which(mdt$Participant == "2019112013401963")] <- 115
mdt$Participant[which(mdt$Participant == "2019112014532376")] <- 108
mdt$Participant[which(mdt$Participant == "2019112016110741")] <- 117
mdt$Participant[which(mdt$Participant == "2019112110260325")] <- 119
mdt$Participant[which(mdt$Participant == "2019112111415316")] <- 110

mdt$Participant[which(mdt$Participant == "2019112112563983")] <- 121
mdt$Participant[which(mdt$Participant == "2019112209583295")] <- 123
mdt$Participant[which(mdt$Participant == "2019112210523539")] <- 125
mdt$Participant[which(mdt$Participant == "2019112213492145")] <- 127
mdt$Participant[which(mdt$Participant == "201911221604385")] <- 320

mdt$Participant[which(mdt$Participant == "2019112217002412")] <- 112
mdt$Participant[which(mdt$Participant == "2019120409523578")] <- 114
mdt$Participant[which(mdt$Participant == "2019120413585457")] <- 129
mdt$Participant[which(mdt$Participant == "201912041554552")] <- 324
mdt$Participant[which(mdt$Participant == "2019120509244570")] <- 116

mdt$Participant[which(mdt$Participant == "2019120512235593")] <- 131
mdt$Participant[which(mdt$Participant == "20191212114750")] <- 118
mdt$Participant[which(mdt$Participant == "2019121212434199")] <- 133
mdt$Participant[which(mdt$Participant == "2019121214503690")] <- 120
mdt$Participant[which(mdt$Participant == "2019121215561995")] <- 330

mdt$Participant[which(mdt$Participant == "201912121703332")] <-
  135   # different from cst
mdt$Participant[which(mdt$Participant == "2019121313154134")] <- 122
mdt$Participant[which(mdt$Participant == "2019121314001724")] <- 124
mdt$Participant[which(mdt$Participant == "2019121315012099")] <- 137
mdt$Participant[which(mdt$Participant == "2019121316322025")] <-
  139 # missed

# miss 371, half of 395

# it should be 132 participants
```

The number of unique participants is as follows:

```{r}
length(unique(mdt$Participant))
```

### Qualtrics

```{r}
# for qualtric survey
qua_raw$participant[which(qua_raw$participant=="2019-11-1309:49:2632")]<-101
qua_raw$participant[which(qua_raw$participant=="2019-11-1311:10:2438")]<-102
qua_raw$participant[which(qua_raw$participant=="2019-11-1313:38:0337")]<-103
qua_raw$participant[which(qua_raw$participant=="2019-11-1314:56:0233")]<-105
qua_raw$participant[which(qua_raw$participant=="2019-11-1316:12:1898")]<-107

qua_raw$participant[which(qua_raw$participant=="2019-11-1808:39:3927")]<-104
qua_raw$participant[which(qua_raw$participant=="2019-11-1811:26:4976")]<-109
qua_raw$participant[which(qua_raw$participant=="2019-11-1812:45:1738")]<-111
qua_raw$participant[which(qua_raw$participant=="2019-11-1813:58:0893")]<-113
qua_raw$participant[which(qua_raw$participant=="2019-11-1814:48:2896")]<-106

qua_raw$participant[which(qua_raw$participant=="2019-11-2013:40:1983")]<-115
qua_raw$participant[which(qua_raw$participant=="2019-11-2014:53:2351")]<-108
qua_raw$participant[which(qua_raw$participant=="2019-11-2016:11:0713")]<-117
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 11:14")]<-119
qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 12:17")]<-110

qua_raw$participant[which(qua_raw$RecordedDate=="11/21/19 13:54")]<-121
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 10:45")]<-123
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 11:30")]<-125
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 14:35")]<-127
qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 16:52")]<-320

qua_raw$participant[which(qua_raw$RecordedDate=="11/22/19 17:40")]<-112
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 12:05")]<-114
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 14:36")]<-129
qua_raw$participant[which(qua_raw$RecordedDate=="12/4/19 16:44")]<-324
qua_raw$participant[which(qua_raw$RecordedDate=="12/5/19 9:59")]<-116

qua_raw$participant[which(qua_raw$RecordedDate=="12/5/19 13:20")]<-131
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 13:23")]<-118
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 14:29")]<-133
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 15:44")]<-120
qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 16:44")]<-330

qua_raw$participant[which(qua_raw$RecordedDate=="12/12/19 17:45")]<-135
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 13:58")]<-122
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 14:47")]<-124
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 16:32")]<-137
qua_raw$participant[which(qua_raw$RecordedDate=="12/13/19 17:04")]<-139
```

Delete the pilot participants from Qualtrics.

```{r}
qua_raw$participant <- as.numeric(qua_raw$participant)

qua <- qua_raw[, -c(1:6, 8:17)] %>%
  filter(Finished == 1) %>%
  filter(participant != "test") %>%
  filter(participant != 0)

length(unique(qua$participant))
# miss one 385
```

The number of unique participants is as follows:

```{r}
length(unique(qua_raw$participant))
```

```{r}
qua$Participant<-as.character(qua$participant)
```

## Gender

### Contrast sensitivity

```{r}
# NA's were all female
cst$Gender[1:4] <- 0

# Make Gender a factor with two levels
cst$Gender <-
  factor(cst$Gender,
         levels = c(0, "m"),
         labels = c("Females", "Males"))
```

### Motion duration

```{r}
# NA's were all female
mdt$Gender[313:316] <- 0

# Make Gender a factor with two levels
mdt$Gender <-
  factor(mdt$Gender,
         levels = c(0, "m"),
         labels = c("Females", "Males"))
```

### Qualtrics

```{r}
qua$sex <- factor(qua$sex,
                  levels = c(2, 1),
                  labels = c("Females", "Males"))
names(qua)[names(qua) == "sex"] <- "Gender"
```

## Threshold estimates

We had preregistered the following exclusion criterion for individual runs:

> We will exclude the run of visual perception tasks with less than 50% accuracy (guess rate).

The marginal error is 1.97*sqrt(p(1-p)/30)=0.18
The 95 confidence intervals are 50% +/- 18% [32% 68%]
Thus, we will exclude runs with less than 68% accuracy.

### Contrast sensitivity

```{r}
which(cst$percent_correct < 0.68)  # 29  30  31  32 371
cst$Participant[which(cst$percent_correct<0.68)] # "111" "111" "111" "111" "393"
```

Excluding these runs:

```{r}
cst <- cst %>% filter(percent_correct >= 0.68)
```

We checked plots of individual cumulative performance by run for anomalous results.

```{r}
# check the cumulative figures of contrast sensitivity for each participant (up tp 366)
# 2019111811264955, 2019112210523539, 2019112217002412,20191205244570, 338, 339, 342, 344, 347, 351, 352, 358, 365, 366, 372, 375, 385, 388, 391, 402, 404, 410, 413, 416, 420, 421, 428 has one run very different from the others
# 350, 379, 431 has two runs very different from the others
# 393 (the 3rd, deleted due to low accuracy),417 (none is deleted) has a weird run
# 2019111812451739 (all deleted) has 4 wrong runs
cst$threshold[which(cst$threshold > 1)]
```

### Motion duration

```{r}
which(mdt$percent_correct < 0.68) # 85  86  87  88 325 326 327 328 480 504 505
mdt$Participant[which(mdt$percent_correct<0.68)] # "114" "114" "114" "114" "383" "383" "383" "383" "422" "428" "428"
```

Excluding these runs:

```{r}
mdt <- mdt %>% filter(percent_correct >= 0.68)
```

## Other task variables

We had preregistered the following exclusion criteria:

> We will exclude final scores of spatial ability, hobbies, and verbal ability data which are zero.

```{r}
which(qua$advoc_num_cor==0)
which(qua$MRT_cor==0)
which(qua$hobfem==0)
which(qua$hobmas==0)
```

No participants had zero scores on `MRT_cor`, the mental rotation measure, `advoc_num_cor`, the vocabulary measure, or on `hobfem` or `hobmas`, the hobby measures.

### Visual acuity

> We will exclude participants whose visual acuity is equal to or worse than 20/40 in HOTV visual acuity chart.

```{r}
# no participant with visual acuity lower than 20/40.
```

**MODIFY TO INDICATE HOW `acuity` measure maps to standard values.**

## Compute threshold summary statistics

We create data that summarize the by-run thresholds across runs.

Specifically, we calculate the median, mean, and standard deviation of the by-run threshold estimates.

### Contrast sensitivity

```{r}
cst_median <- cst %>%
  group_by(Participant, Gender) %>%
  summarise(cst_median = median(threshold),
            cst_mean = mean(threshold),
            cst_sd = sqrt(var(threshold)))
```

### Motion duration

```{r}
mdt_median <- mdt %>%
  group_by(Participant, Gender) %>%
  summarise(mdt_median = median(threshold),
            mdt_mean = mean(threshold),
            mdt_sd = sqrt(var(threshold)))
```

## Merge prior to further cleaning

We then merge the data frames prior to further cleaning.

```{r}
df_vision <-
  full_join(mdt_median, cst_median, by = c("Participant", "Gender"))
```


```{r}
df <- 
  full_join(qua, df_vision, by = c("Participant", "Gender"))  # 131, 132 rows->132 rows?
```

## Clean other variables from Qualtrics

### Race

```{r, clean-race}

df$race <- NA

df$race[df$race_1 == 1] <- "Asian"

df$race[df$race_2 == 1] <- "Black"

df$race[df$race_3 == 1] <- "White"

df$race[df$race_4 == 1] <- "Hispanic/Latino"

df$race[df$race_5 == 1] <- "Native American"

df$race[df$race_6 == 1] <- "Pacific Islander"

df$race[df$race_7 == 1] <- "Prefer not to answer"
```

### Color vision

We defer to another time the task of cleaning the color vision variables.

```{r}
df$colorvision <- NA
```

## Recode `Gender` values

```{r}
df$Gender <- dplyr::recode(df$Gender, Females = 'Female', Males = 'Male')
```

### correct hobby scores

```{r}
hobby_temp<-df %>% select(h1:h60)
df$hobby_mean<-rowMeans(hobby_temp,na.rm=T)
df$hobfem<-rowMeans(hobby_temp[,c(3,8,9,10,14,15,16,19,20,21,26,30,37,43,49,50,53,54,55,56,59,60)],na.rm=T)
df$hobmas<-rowMeans(hobby_temp[,c(1,6,11,17,18,23,25,31,34,35,39,41,44,48,57)],na.rm=T)
df$femscale<-df$hobfem-df$hobby_mean
df$masscale<-df$hobmas-df$hobby_mean
```

# Export

Select data to export.

```{r}
# save data
var <-
  c(
    "Participant",
    "Gender",
    "race",
    "age",
    "schoolyear",
    "major",
    "handedness",
    "glasses",
    "acuity",
    "colorvision",
    "stereo",
    "mdt_median",
    "mdt_mean",
    "mdt_sd",
    "cst_median",
    "cst_mean",
    "cst_sd",
    "advoc_total_score",
    "advoc_num_cor",
    "MRT_cor",
    "MRT_cor_both",
    "hobfem",
    "hobmas",
    "hobby_mean",
    "femscale",
    "masscale"
  )

df1 <- df[, var]
colnames(df1) <-
  c(
    "Participant",
    "Sex",
    "Race",
    "Age",
    "School_year",
    "Major",
    "Handedness",
    "Glasses",
    "Acuity",
    "Color_vision",
    "Stereo",
    "motion_dur_thr",
    "motion_dur_thr_mean",
    "motion_dur_thr_sd",
    "contrast_thr",
    "contrast_thr_mean",
    "contrast_thr_sd",
    "vocab",
    "Vocabulary_scores_cor_num",
    "mental_rot",
    "Mental_Rotation_scores_both",
    "Feminine_hobbies",
    "Masculine_hobbies",
    "hobby_mean",
    "femscale",
    "masscale"
  )
```

## Merge with hobby-specific ratings

```{r}
dfh <- readr::read_csv(file.path(params$processed_data_path, params$hobbies_csv_fn))

# Select Participant ID and individual hobby scores to join with other data
dfh1 <- dfh[,c(1, 167:226)]
dfh1$Participant <- as.character(dfh1$Participant)

df1 <- dplyr::left_join(df1, dfh1, by = 'Participant')
```


## Export combined file

Export the file as a CSV with a date-time stamp. 

```{r}
output_fn <- paste0('combined_', format.Date(Sys.Date()), '.csv')
write.csv(df1,
          file.path(params$output_path, output_fn),
          row.names = FALSE)
```

