---
title: "Relative Weight Analysis (RWA)"
output: 
  html_document:
    toc: true
    toc_depth: 2
---

### Setup

```{r set-seed}
set.seed(1234)
n_boots <- 10000
library(tidyverse) # For pipe '%>%'
library(mediation)
```

### Import and clean data

```{r}
df <- readr::read_csv(file.path("csv/mr-contr-motion-sex.csv"))

# Requires all variables be numeric so we recode Sex with Female = 0, Male = 1.
df <- df %>%
  dplyr::mutate(., male = if_else(Sex == "Male", 1, 0)) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male)
```

#### Create Sex:log_motion variable

```{r add-sex-motion-interaction}
df <- df %>%
  dplyr::mutate(., male_motion = male * log_motion) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male, male_motion)
```

Compute residuals of `male_motion ~ 1 + male + log_motion` in order to estimate relative weight properly.

```{r}
male_motion_lm <- lm(formula = male_motion ~ 1 + male + log_motion, data = df)

male_motion_resid <- resid(male_motion_lm)

df <- df %>%
  dplyr::mutate(., male_motion_r = male_motion_resid) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male, male_motion_r)
```

#### Grab variable names

```{r}
predictors <- names(df)[2:length(df)] 
```

#### Verify data are not singular

```{r data-singular}
eigen(cor(df))
```

### Run conventional regression analyses

```{r}
fit1 <- lm(mental_rot ~ 1 + log_contrast + log_motion + male, data = df)
summary(fit1)
plot(fit1) # residual plots for OLS; use <Return> key to cycle through plots in console.
```

```{r}
fit2 <- psych::corr.test(df)
print(fit2)
```

#### Load helper functions

```{r define-helper-functions}
# First up is the RWA function for a traditional multiple regression analysis
multRegress <- function(mydata) {
  numVar <<- NCOL(mydata)
  Variables <<- names(mydata)[2:numVar]
  
  mydata <- cor(mydata, use = "pairwise.complete.obs")
  RXX <- mydata[2:numVar, 2:numVar]
  RXY <- mydata[2:numVar, 1]
  
  RXX.eigen <- eigen(RXX)
  D <- diag(RXX.eigen$val)
  delta <- sqrt(D)
  
  lambda <- RXX.eigen$vec %*% delta %*% t(RXX.eigen$vec)
  lambdasq <- lambda ^ 2
  beta <- solve(lambda) %*% RXY
  rsquare <<- sum(beta ^ 2)
  
  RawWgt <- lambdasq %*% beta ^ 2
  import <- (RawWgt / rsquare) * 100
  
  result <<-
    data.frame(Variables,
               Raw.RelWeight = RawWgt,
               Rescaled.RelWeight = import)
}

# Next up, are functions for the bootstrapping options
multBootstrap <- function(mydata, indices) {
  mydata <- mydata[indices, ]
  multWeights <- multRegress(mydata)
  return(multWeights$Raw.RelWeight)
}

multBootrand <- function(mydata, indices) {
  mydata <- mydata[indices, ]
  multRWeights <- multRegress(mydata)
  multReps <- multRWeights$Raw.RelWeight
  randWeight <- multReps[length(multReps)]
  randStat <- multReps[-(length(multReps))] - randWeight
  return(randStat)
}

multBootcomp <- function(mydata, indices, pred_index = 1) {
  mydata <- mydata[indices, ]
  multCWeights <- multRegress(mydata)
  multCeps <- multCWeights$Raw.RelWeight
  comp2Stat <-
    multCeps - multCeps[pred_index] # Need to change the number in brackets to reflect which predictor is focal
  comp2Stat <-
    comp2Stat[-pred_index] # # If 1st predictor, then [1], if the 3rd predictor, then [3]
  predictors2 <<-
    predictors[-pred_index] # Change number in all three lines (88:90) of code
  return(comp2Stat)
}

mybootci <- function(x, FUN2 = multBootcomp) {
  boot::boot.ci(multBoot,
          conf = 0.95,
          type = "bca",
          index = x) # using bias corrected and accelerated CIs
}

runBoot <- function(num) {
  INDEX <- 1:num
  test <- lapply(INDEX, FUN = mybootci)
  test2 <- t(sapply(test, '[[', i = 4)) #extracts confidence interval
  CIresult <<-
    data.frame(Variables,
               CI.Lower.Bound = test2[, 4],
               CI.Upper.Bound = test2[, 5])
}

myRbootci <- function(x) {
  boot::boot.ci(multRBoot,
          conf = 0.95,
          type = "bca",
          index = x)
}

runRBoot <- function(num) {
  INDEX <- 1:num
  test <- lapply(INDEX, FUN = myRbootci)
  test2 <- t(sapply(test, '[[', i = 4))
  CIresult <<-
    data.frame(predictors,
               CI.Lower.Bound = test2[, 4],
               CI.Upper.Bound = test2[, 5])
}

myCbootci <- function(x) {
  boot::boot.ci(multC2Boot,
          conf = 0.95,
          type = "bca",
          index = x)
}

runCBoot <- function(num) {
  INDEX <- 1:num
  test <- lapply(INDEX, FUN = myCbootci)
  test2 <- t(sapply(test, '[[', i = 4))
  CIresult <<-
    data.frame(predictors2,
               CI.Lower.Bound = test2[, 4],
               CI.Upper.Bound = test2[, 5])
}

myGbootci <- function(x) {
  boot::boot.ci(groupBoot,
          conf = 0.95,
          type = "bca",
          index = x)
}

runGBoot <- function(num) {
  INDEX <- 1:num
  test <- lapply(INDEX, FUN = myGbootci)
  test2 <- t(sapply(test, '[[', i = 4))
  CIresult <<-
    data.frame(predictors,
               CI.Lower.Bound = test2[, 4],
               CI.Upper.Bound = test2[, 5])
}
```

#### Run the RWA

```{r rwa-analysis}
multRegress(df)
(RW.Results <-
    result) # create new objects that saves results of RW analysis.
# using the () just tells R to print the results and create the object.

RSQ.Results <- rsquare
```

#### Run bootstrapping to estimate SEs

```{r rwa-bootstrap}
#Bootstrapped Confidence interval around the individual relative weights
#Please be patient -- This can take a few minutes to run
multBoot <-
  boot::boot(df, multBootstrap, n_boots) # n_boots is the # of replications;
# you can change to other values.
multci <- boot::boot.ci(multBoot, conf = 0.95, type = "bca")
runBoot(length(df[, 2:numVar]))
CI.Results <- CIresult

#Bootstrapped Confidence interval tests of Significance
#Please be patient -- This can take a few minutes to run
randVar <- rnorm(nrow(df[, 1]), 0, 1)
randData <- cbind(df, randVar)
multRBoot <- boot::boot(randData, multBootrand, n_boots)
multRci <- boot::boot.ci(multRBoot, conf = 0.95, type = "bca")
runRBoot(length(randData[, 2:(numVar - 1)]))
CI.Significance <- CIresult
```

#### Relative weights for full model

```{r}
#R-squared For the Model
RSQ.Results

#The Raw and Rescaled Weights
RW.Results

#BCa Confidence Intervals around the raw weights
CI.Results

#BCa Confidence Interval Tests of significance
#If Zero is not included, Weight is Significant
CI.Significance
```

### Run the RWA on the trimmed data

We deleted two female participants with very low motion duration thresholds. Here we examine whether that changes the relative weights.

#### Import and clean data

```{r}
df <- readr::read_csv(file.path("csv/mr-contr-motion-sex-trimmed.csv"))

# Requires all variables be numeric so we recode Sex with Female = 0, Male = 1.
df <- df %>%
  dplyr::mutate(., male = if_else(Sex == "Male", 1, 0)) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male)

df <- df %>%
  dplyr::mutate(., male_motion = male * log_motion) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male, male_motion)

male_motion_lm <- lm(formula = male_motion ~ 1 + male + log_motion, data = df)

male_motion_resid <- resid(male_motion_lm)

df <- df %>%
  dplyr::mutate(., male_motion_r = male_motion_resid) %>%
  dplyr::select(., mental_rot, log_contrast, log_motion, male, male_motion_r)
```

#### Run the RWA

```{r rwa-analysis-trimmed}
multRegress(df)
(RW.Results <-
    result) # create new objects that saves results of RW analysis.
# using the () just tells R to print the results and create the object.

RSQ.Results <- rsquare
```

#### Run bootstrapping to estimate SEs

```{r rwa-bootstrap-trimmed}
#Bootstrapped Confidence interval around the individual relative weights
#Please be patient -- This can take a few minutes to run
multBoot <-
  boot::boot(df, multBootstrap, n_boots) # n_boots is the # of replications;
# you can change to other values.
multci <- boot::boot.ci(multBoot, conf = 0.95, type = "bca")
runBoot(length(df[, 2:numVar]))
CI.Results <- CIresult

#Bootstrapped Confidence interval tests of Significance
#Please be patient -- This can take a few minutes to run
randVar <- rnorm(nrow(df[, 1]), 0, 1)
randData <- cbind(df, randVar)
multRBoot <- boot::boot(randData, multBootrand, n_boots)
multRci <- boot::boot.ci(multRBoot, conf = 0.95, type = "bca")
runRBoot(length(randData[, 2:(numVar - 1)]))
CI.Significance <- CIresult
```

#### Relative weights for full model (trimmed data)

```{r results-trimmed}
#R-squared For the Model
RSQ.Results

#The Raw and Rescaled Weights
RW.Results

#BCa Confidence Intervals around the raw weights
CI.Results

#BCa Confidence Interval Tests of significance
#If Zero is not included, Weight is Significant
CI.Significance
```