---
title: "Data explorations for Rochester symposium"
output: html_notebook
date: "`r Sys.time()`"
---

```{r}
library(tidyverse)
library(ggplot2)
```

# Purpose

# Load & clean data

## Motion data

Let's pick one participant who is highly variable: 20191118083974.

```{r}
s1 <- readr::read_csv("~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/passed_qa/20191118083974_motion_temporal_threshold.csv")
```

And a second who is very consistent: 2019112209583295

```{r}
s2 <- readr::read_csv("~/Box Sync/Project_Sex_difference_on_Motion_Perception/data/passed_qa/2019112209583295_motion_temporal_threshold.csv")
```

### Clean the data

```{r}
clean_motion_df <- function(df) {
  require(tidyverse)
  if (!is.data.frame(df)) stop("Not a valid data frame.")
  
  df_clean <- df %>%
    dplyr::mutate(., run = run_n + 1) %>%
    dplyr::rename(., corr = correct,
                  dur_s = FWHM)
  
  df_clean <- df_clean %>%
    dplyr::select(.,
                  run,
                  trial_n,
                  dur_s,
                  corr,
                  rt) %>%
    dplyr::mutate(., run = ordered(run))
  df_clean
}
```

```{r}
s1 <- clean_motion_df(s1)
s2 <- clean_motion_df(s2)
```

# Visualize

```{r}
s1 %>% ggplot(.) +
  aes(x = trial_n, y = dur_s, color = run) +
  geom_point() +
  geom_smooth()
```

```{r}
s2 %>% ggplot(.) +
  aes(x = trial_n, y = dur_s, color = run) +
  geom_point() +
  geom_smooth()
```

# Quantify variability

## Duration at trial = 30

```{r}
s1_tr30 <- dplyr::filter(s1, trial_n == 30)
(s1_tr30_sd <- sd(s1_tr30$dur_s))
(s1_tr30_rng <- max(s1_tr30$dur_s) - min(s1_tr30$dur_s))
```

```{r}
s2_tr30 <- dplyr::filter(s2, trial_n == 30)
(s2_tr30_sd <- sd(s2_tr30$dur_s))
(s2_tr30_rng <- max(s2_tr30$dur_s) - min(s2_tr30$dur_s))
```

## Cross-correlation across runs

```{r}
s1_1 <- s1$dur_s[s1$run == 1]
s1_2 <- s1$dur_s[s1$run == 2]
s1_3 <- s1$dur_s[s1$run == 3]
s1_4 <- s1$dur_s[s1$run == 4]
(s1_runs <- cbind(s1_1, s1_2, s1_3, s1_4))
```

```{r}
cor(s1_runs)
```

```{r}
s2_1 <- s2$dur_s[s2$run == 1]
s2_2 <- s2$dur_s[s2$run == 2]
s2_3 <- s2$dur_s[s2$run == 3]
s2_4 <- s2$dur_s[s2$run == 4]
(s2_runs <- cbind(s2_1, s2_2, s2_3, s2_4))
```

```{r}
cor(s2_runs)
```

# Discussion

These measures seem to capture the differences we see in the plots, so the next step is to write functions that extract the statistics and gather them across the dataset.

# Next steps

```{r}
compute_within_p_var <- function(df) {
  tr30 <- dplyr::filter(df, trial_n == 30)
  tr30_sd <- sd(tr30$dur_s)
  tr30_rng <- max(tr30$dur_s) - min(tr30$dur_s)
  
  r1 <- df$dur_s[df$run == 1]
  r2 <- df$dur_s[df$run == 2]
  r3 <- df$dur_s[df$run == 3]
  r4 <- df$dur_s[df$run == 4]
  
  these_runs <- cbind(r1, r2, r3, r4)
  cor_vals <- cor(these_runs)
  mean_cor <- mean(cor_vals[1,2], 
                   cor_vals[1,3], 
                   cor_vals[1,4],
                   cor_vals[2,3], 
                   cor_vals[2,4], 
                   cor_vals[3,4])
  med_cor <- median(cor_vals[1,2], 
                    cor_vals[1,3], 
                    cor_vals[1,4],
                    cor_vals[2,3], 
                    cor_vals[2,4], 
                    cor_vals[3,4])
  data.frame(tr_30_sd = tr30_sd, tr30_rng = tr30_rng,
             mean_cor = mean_cor, med_cor = med_cor)
  cor_vals
}
```

