---
title: "Post-processing Quality Assurance (QA)"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
params:
  box_path: "~/Box Sync"
  data_path: "/Project_Sex_difference_on_Motion_Perception/data"
  contrast_raw_path: "/raw_data/contrast_sensitivity_task_data"
  motion_raw_path: "/raw_data/motion_temporal_threshold_data"
  passed_qa_path: "/passed_qa"
  failed_qa_path: "/failed_qa"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE,
                      message = FALSE)

# Manage package dependencies
if (!require(pacman)) {
  install.packages("pacman")
}

library(tidyverse)
library(qualtRics)
```

# Purpose

This script describes the process for doing quality assurance (QA) review on each session.

To render, enter `rmarkdown::render("analysis/session_qa.Rmd", params = list(box_path = "<YOUR_BOX_PATH>"))`, substituting the path to your Box folder on your local machine.
On Mac OS the default is "~/Box Sync".

# Background

1. There are two data files for each participant:
  - One for the Abramov et al contrast sensitivity task `~/Box\ Sync/Project_Sex_difference_on_Motion_Perception/data/contrast_sensitivity_task_data/`
  - One for the Murray et al temporal threshold task `~/Box\ Sync/Project_Sex_difference_on_Motion_Perception/data/motion_sensitivity_task_data/`
2. There is survey data for each participant in `~/Box\ Sync/Project_Sex_difference_on_Motion_Perception/data/qualtrics_data/`
3. There are four runs for each of two computer-based tasks, each run consisting of $n=30$ trials.
4. The computer-based tasks record the participant gender.
6. The data files record the participant ID and the participant ID matches the initial portion of the file name.
7. The data files include the most essential variables for analysis.

## QA steps

1. For each of the computer tasks
  - List the `*.csv` files
  - Look inside the files and determine the following:
      - Does the participant ID match the ID in the file name?
      - Is the participant ID in the file?
      - Does the file have enough trials ($n=30$ for 4 runs)?
      - Does the file have the key variables needed for analysis?
      - Does the file include a variable for gender?
  <!-- - If the answer to all of these questions is yes, then -->
  <!--     - Copy the file(s) to a `pass_qa` folder. -->
  <!-- - If the answer is no, then -->
  <!--     - Copy the file(s) to a `fails_qa` folder. -->
2. A separate R Markdown document should address the file(s) that fail QA. If the failures can be addressed, the document should do so and then copy the corrected data file to the `pass_qa` folder.

# Implementation

## Create lists of `.csv` files

### Contrast

```{r contrast-csvs}
contr_data_path <- paste0(params$box_path, 
                          params$data_path, 
                          params$contrast_raw_path)
if (dir.exists(contr_data_path)) {
  contrast_csvs <- list.files(contr_data_path, pattern = "\\.csv$")
  contrast_csvs %>% 
    knitr::kable(.)
} else {
  message(paste0("No data files exist in ", contr_data_path))
}
```

There are `r length(contrast_csvs)` .csv files for the Abramov contrast sensitivity task.

### Motion

```{r motion-csvs}
motion_data_path <- paste0(params$box_path, 
                           params$data_path, 
                           params$motion_raw_path)
if (dir.exists(motion_data_path)) {
  motion_csvs <- list.files(motion_data_path, pattern = "\\.csv$")
  motion_csvs %>% knitr::kable(.)  
} else {
  message(paste0("No data files exist in ", motion_data_path))
}

```

There are `r length(motion_csvs)` .csv files for the Murray motion temporal threshold task.

## File by file QA

```{r define-qa-functions}
has_enough_trials <- function(data_df, n_trials = 4*30) {
  dim(data_df)[1] >= n_trials
}

observer_id_in_file <- function(data_df, task='contr') {
  if (task=='contr') {
    sum(!(is.na(data_df$Participant))) == length(data_df$Participant)
  } else {
    sum(!(is.na(data_df$observer))) == length(data_df$observer)
  }
}

gender_in_file <- function(data_df, task = 'contr') {
  if (task == 'contr') {
    sum(!(is.na(data_df$Gender))) > 0    
  } else {
    sum(!(is.na(data_df$gender))) > 0 
  }
}

sub_id_matches_fn <- function(data_fn, task='contr') {
  data_df <- readr::read_csv(data_fn)
  if (task=='contr') {
    sub_id <- as.character(data_df$Participant)
  } else {
    sub_id <- as.character(data_df$observer)
  }
  sub_id_fn <- stringr::str_extract(basename(data_fn), "[0-9]+")
  sum(sub_id == sub_id_fn) == length(sub_id)
} 

essential_vars_in_file <- function(data_df, task = 'contr') {
  if (task == 'contr') {
    essential_vars <- c("correctAns", "loop_trial.intensity", 
                        "loop_trial.thisN", "Participant", "Gender", "resp.rt")
  } else {
    essential_vars <- c("run_n", "correct", 
                        "trial_n", "stim_secs", "correct", 
                        "rt", "observer", "FWHM", "actual_frame")
  }
  (sum(essential_vars %in% names(data_df)) == length(essential_vars))
}

make_qa_df <- function(data_fn, task = 'contr') {
  fn <- basename(data_fn)
  data_df <- readr::read_csv(data_fn)
  data.frame(fn,
             id_matches_fn = sub_id_matches_fn(data_fn, task),
             id_in_file = observer_id_in_file(data_df, task),
             enough_trials = has_enough_trials(data_df),
             has_key_vars = essential_vars_in_file(data_df, task),
             gender_var = gender_in_file(data_df, task)
             )
}
```

### Contrast

```{r contr-fns}
contr_fns <- list.files(contr_data_path, 
                        pattern = "\\.csv$", full.names = TRUE)
dfl <- lapply(contr_fns, make_qa_df, task = "contr")
contrast_file_qa <- Reduce(function(x,y) merge(x,y, all=TRUE), dfl)
contrast_file_qa %>% knitr::kable(.)
```

### Motion

```{r}
motion_fns <- list.files(motion_data_path, 
                         pattern = "\\.csv$", full.names = TRUE)
dfl <- lapply(motion_fns, make_qa_df, task = "motion")
motion_file_qa <- Reduce(function(x,y) merge(x,y, all=TRUE), dfl)
motion_file_qa %>% knitr::kable(.)
```

## Examine files that pass or fail QA

### Files that pass QA

```{r}
motion_file_qa <- motion_file_qa %>%
  dplyr::mutate(., pass_qa = id_matches_fn & 
                  id_in_file & enough_trials & 
                  has_key_vars & gender_var)

contrast_file_qa <- contrast_file_qa %>%
  dplyr::mutate(., pass_qa = id_matches_fn & 
                  id_in_file & enough_trials & 
                  has_key_vars & gender_var)
```

There are `r sum(contrast_file_qa$pass_qa)` contrast task files that pass file-level QA.

There are `r sum(motion_file_qa$pass_qa)` motion task files that pass file-level QA.

### Files that fail QA

There are `r sum(!contrast_file_qa$pass_qa)` contrast task files that fail file-level QA.

```{r}
contrast_file_qa %>%
  dplyr::filter(., !pass_qa) %>%
  knitr::kable(.)
```

There are `r sum(!motion_file_qa$pass_qa)` motion task files that fail file-level QA.

```{r}
motion_file_qa %>%
  dplyr::filter(., !pass_qa) %>%
  knitr::kable(.)
```

## Copy files

Copy files to directories.

```{r, message=FALSE, warning=FALSE, include=FALSE}
# generate full file path to target directory
passed_qa_full_path <- paste0(params$box_path, params$data_path, params$passed_qa_path)
passed_qa_full_path

# Add full file paths to data frames
motion_file_qa <- motion_file_qa %>%
  dplyr::mutate(., full_path = paste0(motion_data_path, "/", fn)) %>%
  dplyr::mutate(., qa_full_path = paste0(params$box_path, params$data_path,
                                         params$passed_qa_path, "/", fn)) %>%
  dplyr::mutate(., failed_qa_full_path = paste0(params$box_path, params$data_path,
                                         params$failed_qa_path, "/", fn))


contrast_file_qa <- contrast_file_qa %>%
  dplyr::mutate(., full_path = paste0(contr_data_path, "/", fn)) %>%
  dplyr::mutate(., qa_full_path = paste0(params$box_path, params$data_path,
                                         params$passed_qa_path, "/", fn)) %>%
  dplyr::mutate(., failed_qa_full_path = paste0(params$box_path, params$data_path,
                                         params$failed_qa_path, "/", fn))

# Helper function to handle copying
copy_files_to_qa_target <- function(df_i, df) {
  if (df$pass_qa[df_i]) {
    file.copy(from = df$full_path[df_i], df$qa_full_path[df_i], overwrite = TRUE)
  } else {
    file.copy(from = df$full_path[df_i], df$failed_qa_full_path[df_i], overwrite = TRUE)
  }
}

# Now copy
purrr::map(1:dim(motion_file_qa)[1], copy_files_to_qa_target, motion_file_qa)
purrr::map(1:dim(contrast_file_qa)[1], copy_files_to_qa_target, contrast_file_qa)
```

