---
title: "plot_for_VSS"
author: "Yiming Qian & Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
params:
  data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  hobby_data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data"
  csv_fn: "combined_2021-04-30.csv"
  outlier_sd_thresh: 3.0
---

# Purpose

This document generates visualizations for a poster by Qian & Gilmore, 2021.

Qian, Y. & Gilmore, R.O. (2021, May). Sex differences in visual processing: Does it relate to cognition or other behaviors? Poster presented at the Virtual Vision Sciences Society (V-VSS) 2021 meeting.

# Setup

Set chunk options and load libraries.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(add2ggplot)
library(gridExtra)
library(Hmisc)
```

# Import data and clean

```{r load}
# load the data and make each variable right
df1 <- readr::read_csv(file.path(params$data_path, params$csv_fn)) 
```

Remove outliers using a threshold based on the number of standard deviations from the mean.

Here we use `r params$outlier_sd_thresh`.

```{r}
# define a function to remove outliers
FindOutliers <-
  function(data,
           sd_thresh = as.numeric(params$outlier_sd_thresh)) {
    sd = sd(data, na.rm = T)
    mean = mean(data, na.rm = T)
    # we identify extreme outliers
    extreme.threshold.upper = (sd * sd_thresh) + mean
    extreme.threshold.lower = -(sd * sd_thresh) + mean
    result <-
      which(data > extreme.threshold.upper |
              data < extreme.threshold.lower)
    print(result)
  }

outliers <- lapply(df1, FindOutliers)
outliers
```

```{r}
df2 <- df1
df2$contrast_thr[outliers[['contrast_thr']]] <- NA
df2$motion_dur_thr[outliers[['motion_dur_thr']]] <- NA

df2 <- df2 %>%
  dplyr::mutate(.,
                log_contrast = log(contrast_thr),
                log_motion = log(motion_dur_thr))
# df2 <- df1[-c(outliers[['contrast_thr']], outliers[['motion_dur_thr']]),] # we cannot use this code, because there is overlap in the outliers of these two threshold. It will delete one good data.
```

# Plots

```{r}
p1 <- ggplot(df2, aes(x = Sex, y = log_contrast, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  theme(legend.position = "none") +
  ylab("Contrast Sensitivity")
```


```{r}
p2 <- ggplot(df2, aes(x = Sex, y = log_motion, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  theme(legend.position = "none") +
  ylab("Motion Perception")
```

```{r}
p3 <- ggplot(df2, aes(x = Sex, y = mental_rot, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  ylab("Mental Rotation Scores")
```


```{r}
p4 <- ggplot(df2, aes(x = Sex, y = vocab, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  theme(legend.position = "none") +
  ylab("Vocabulary Scores")
```


```{r}
p5 <- ggplot(df2, aes(x = Sex, y = masscale, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  theme(legend.position = "none") +
  ylab("Masculine Hobbies")
```


```{r}
p6 <- ggplot(df2, aes(x = Sex, y = femscale, color = Sex)) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 2,
    position = position_dodge(0.8)
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    position = position_dodge(0.8),
    width = .5
  ) +
  scale_fill_discrete("Sex") +
  theme_classic() +
  ylab("Feminine Hobbies")
```


```{r}
p = grid.arrange(layout_matrix = rbind(c(1, 1, 2, 2, 3, 3, 3),
                                       c(4, 4, 5, 5, 6, 6, 6)), p1, p2, p3, p4, p5, p6)
#labels = c("a", "b", "c")
ggsave(
  plot = p,
  filename = paste0(here::here(), "/pg2.png"),
  units = "in",
  height = 12,
  width = 18,
  dpi = 600
)
```


```{r}
df_corr <- df2 %>%
  dplyr::select(Sex,
                Age,
                log_contrast,
                log_motion,
                mental_rot,
                vocab,
                #      Masculine_hobbies,
                #    Feminine_hobbies,
                femscale,
                masscale)

df_complete <- df_corr[stats::complete.cases(df_corr), ]

# Set the number of digits to display in the tables
options(digits = 2)
```


```{r}
df_complete_F <- df_complete %>%
  dplyr::filter(., Sex == 'Females') 

df_complete_M <- df_complete %>%
  dplyr::filter(., Sex == 'Males') 

df_corr_m <-df_complete %>%
  dplyr::filter(., Sex == 'Males') %>%
  dplyr::select(., -Sex)

df_corr_f <-df_complete %>%
  dplyr::filter(., Sex == 'Females') %>%
  dplyr::select(., -Sex)

corr_M <- Hmisc::rcorr(as.matrix(df_corr_m), type = c("pearson"))
```

Create a function to generate scatter plots.

```{r}
sex_diff_scatter <-
  function(df,
           x_var,
           y_var,
           x_rev = FALSE,
           y_rev = FALSE,
           an_f = "",
           an_m = "",
           anx = NULL,
           any = NULL,
           x_lab = "X axis",
           y_lab = "Y axis",
           square_axis = TRUE) {
    
    require(tidyverse)
    require(ggExtra)
    
    x_var_s <- sym(x_var)
    y_var_s <- sym(y_var)
    
    p <- ggplot(df) +
      aes(
        x = !!x_var_s,
        y = !!y_var_s,
        group = Sex,
        color = Sex
      ) +
      geom_point() +
      xlab(x_var) +
      ylab(y_var) +
      stat_smooth(method = "lm", na.rm = TRUE) +
      theme_classic2() +
      theme(legend.position = "bottom",
            legend.title = element_blank()) +
      xlab(x_lab) +
      ylab(y_lab) +
      annotate(
        "text",
        x = anx,
        y = any,
        label = c(an_f, an_m),
        color = c('red', 'darkturquoise')
      )
    
    if (square_axis)
    {
      p + coord_fixed()
    }
    
    if (stringr::str_detect(x_var, 'hobbies')) {
      p <- p + xlim(1, 5)
    }
    if (stringr::str_detect(y_var, 'hobbies')) {
      p <- p + ylim(1, 5)
    }
    
    # Reverse scale for threshold measures?
    if (x_rev)
      p <- p + scale_x_reverse()
    if (y_rev)
      p <- p + scale_y_reverse()
    
    
    p1
  }
```


```{r sex-diff-corr-sum-function}
sex_diff_corr_summ <- function(x_var, y_var, print_table = TRUE) {
  require(tidyverse) # for %>%
  
  corr_all_df <- tibble::tibble(
    cor_coef = corr_all$r[x_var, y_var],
    p_val = corr_all$P[x_var, y_var],
    n =  corr_all$n[x_var, y_var],
    pop = "Both"
  )
  males_df <- tibble::tibble(
    cor_coef = corr_M$r[x_var, y_var],
    p_val = corr_M$P[x_var, y_var],
    n =  corr_M$n[x_var, y_var],
    pop = "Males"
  )
  
  females_df <- tibble::tibble(
    cor_coef = corr_F$r[x_var, y_var],
    p_val = corr_F$P[x_var, y_var],
    n =  corr_F$n[x_var, y_var],
    pop = "Females"
  )
  
  df <- rbind(corr_all_df, males_df, females_df)
  
  df <- df %>%
    mutate(., stars = if_else(p_val < .005, "***",
                              if_else(
                                p_val < .01, "**",
                                if_else(p_val < .05, "*", " ns")
                              )))
  
  
  if (print_table) {
    kableExtra::kable(df, format = 'html') %>%
      kableExtra::kable_styling()
  } else {
    df
  }
}
```


```{r}
df_corr <- df_complete %>%
  dplyr::select(.,-Sex)

corr_all <- Hmisc::rcorr(as.matrix(df_corr), type = c("pearson"))
```


```{r}
df_corr_m <- df_complete %>%
  dplyr::filter(., Sex == 'Males') %>%
  dplyr::select(.,-Sex)

corr_M <- Hmisc::rcorr(as.matrix(df_corr_m), type = c("pearson"))

df_corr_f <- df_complete %>%
  dplyr::filter(., Sex == 'Females') %>%
  dplyr::select(.,-Sex)

corr_F <- Hmisc::rcorr(as.matrix(df_corr_f), type = c("pearson"))
```


```{r motion-duration-contrast-sens}
corr_df <- sex_diff_corr_summ("log_motion",
                              "log_contrast", print_table = FALSE)

sex_diff_scatter(
  df_complete,
  "log_motion",
  "log_contrast",
  x_rev = TRUE,
  y_rev = TRUE,
  # "r=0.22*",
  # "r=0.54***",
  paste0(
    "r = ",
    format(corr_df$cor_coef[3], digits = 2, nsmall = 2),
    corr_df$stars[3]
  ),
  paste0(
    "r = ",
    format(corr_df$cor_coef[2], digits = 2, nsmall = 2),
    corr_df$stars[2]
  ),
  c(-1.9, -2.04),
  c(-1.4, -1.98),
  "Motion threshold",
  "Contrast threshold"
)

sex_diff_corr_summ("log_motion",
                   "log_contrast")
```
