---
title: "Sex differences in vision data: Exclude outliers"
author: "Yiming Qian & Rick Gilmore"
date: "`r Sys.time()`"
css: report.css
output: 
  html_document:
    self_contained: yes
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
params:
  data_path: "~/Box/Project_Sex_difference_on_Motion_Perception/data/processed_data"
  csv_fn: "data_output_Oct2020.csv"
  outlier_sd_thresh: 2.5
---

# Purpose

This document shows our analyses following the preregistered plan.
It also shows the results of trimming all cases whose scores on either of the visual perception measures exceed `r params$outlier_sd_thresh` SDs from the pooled mean.

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sjPlot)  # create publishable table
library(pwr)
library(Hmisc)
library(ggpubr)
library(pwr)
library(ggExtra)
library(mediation)
```

# Analysis

## Import

We import data previously cleaned to remove cases where accuracy is lower than the guess rate and any zero scores in the survey measures. 

```{r load}
# load the data and make each variable right
df1 <- readr::read_csv(file.path(params$data_path, params$csv_fn)) 
```

## Rename variables

We rename some of the variables to make the exposition clearer.

```{r, eval=FALSE}
df1 <- df1 %>%
  dplyr::rename(., 'motion_thr' = 'Motion_duration_Threshold',
                'contrast_thr' = 'Contrast_Sensitivity_Threshold',
                'mental_rot' = 'Mental_Rotation_scores',
                'mental_rot_both' = 'Mental_Rotation_scores_both',
                'vocab' = 'Vocabulary_scores',
                'vocab_num' = 'Vocabulary_scores_cor_num')
```


## Exclude outliers

Detect outliers three sd out of mean.

```{r}
# define a function to remove outliers
FindOutliers <- function(data, sd_thresh = as.numeric(params$outlier_sd_thresh)) {
  sd = sd(data, na.rm = T)
  mean = mean(data, na.rm = T)
  # we identify extreme outliers
  extreme.threshold.upper = (sd * sd_thresh) + mean
  extreme.threshold.lower = -(sd * sd_thresh) + mean
  result <-
    which(data > extreme.threshold.upper |
            data < extreme.threshold.lower)
  print(result)
}

a <- lapply(df1, FindOutliers)
a
```

Question: Do we care about outliers in `Age`, `Color_vision`, or `Stereo` vision?

ROG Answer: Probably not. We _might_ care about outliers in visual acuity, though.

So, let's do some quick plots to see what's going on.

```{r}
df1 %>% 
  ggplot(.) +
  aes(y = Acuity, x = Sex) +
  geom_violin() +
  ggtitle('Visual acuity by sex: All participants')
```

```{r}
df1[-a[['Acuity']],] %>%
  ggplot(.) +
  aes(y = Acuity, x = Sex) +
  geom_violin() +
  ggtitle('Visual acuity by sex: Outliers excluded')
```

```{r}
df1 %>% 
  ggplot(.) +
  aes(y = Motion_duration_Threshold, x = Sex) +
  geom_violin() +
  ggtitle('Motion_duration_Threshold by sex: All participants')
```

```{r}
df1[-a[['Motion_duration_Threshold']],] %>%
  ggplot(.) +
  aes(y = Motion_duration_Threshold, x = Sex) +
  geom_violin() +
  ggtitle('Motion_duration_Threshold: Outliers excluded')

df1$Motion_duration_Threshold[a[['Motion_duration_Threshold']]]
```

```{r}
df1 %>% 
  ggplot(.) +
  aes(y = Contrast_Sensitivity_Threshold, x = Sex) +
  geom_violin() +
  ggtitle('Contrast_Sensitivity_Threshold by sex: All participants')
```

```{r}
df1[-a[['Contrast_Sensitivity_Threshold']],] %>%
  ggplot(.) +
  aes(y = Contrast_Sensitivity_Threshold, x = Sex) +
  geom_violin() +
  ggtitle('Contrast_Sensitivity_Threshold: Outliers excluded')

df1$Contrast_Sensitivity_Threshold[a[['Contrast_Sensitivity_Threshold']]]
```

```{r}
#boxplot(df1$Motion_duration_Threshold)
# check Flag_MRT
# 
# df1$Contrast_Sensitivity_Threshold[a[[4]]] # 4 14 96
# #boxplot(df1$Contrast_Sensitivity_Threshold)
```

Exclude outliers
```{r}
df2 <- df1
df2$Contrast_Sensitivity_Threshold[a[['Contrast_Sensitivity_Threshold']]] <- NA
df2$Motion_duration_Threshold[a[['Motion_duration_Threshold']]] <- NA
```
I excluded three outliers in `Motion_duration_Threshold` and two outliers in `Contrast_Sensitivity_Threshold`.

Further exclude two male "outliers" of motion duration threshold
```{r}
df3.m <- df2 %>% filter(Sex=="Males")
df3.f <- df2 %>% filter(Sex=="Females")

a_m <- lapply(df3.m, FindOutliers)
a_m

df3.m$Motion_duration_Threshold[a_m[['Motion_duration_Threshold']]] <- NA
df3<-rbind(df3.m,df3.f)
```


## Check distributions

Preliminary tests to check assumptions underlying  statistical tests.

<!-- 1. Is the covariation linear?  -->

<!-- From the plot below, check whether the relationship is linear. In the situation where the scatter plots show curved patterns, we are dealing with nonlinear association between the two variables. -->

Do the data follow a normal distributions?

Use Shapiro-Wilk normality test, `shapiro.test()` and look at the normality plot —> R function: `ggpubr::ggqqplot()`. 

The Shapiro-Wilk test can be performed as follows:
- Null hypothesis: the data are normally distributed
- Alternative hypothesis: the data are not normally distributed

```{r}
# Shapiro-Wilk normality test 
shapiro.test(df2$Motion_duration_Threshold) # => p <0.001
shapiro.test(df2$Contrast_Sensitivity_Threshold) # => p <0.001
shapiro.test(df2$Vocabulary_scores) # => p <0.001
shapiro.test(df2$Vocabulary_scores_cor_num) # => p <0.001
shapiro.test(df2$Mental_Rotation_scores) # => p <0.001
shapiro.test(df2$Mental_Rotation_scores_both) # => p <0.001
shapiro.test(df2$Feminine_hobbies) # => p >0.05
shapiro.test(df2$Masculine_hobbies) # => p >0.05
```


We use a strict Bonferroni-style criterion of $p<0.0125$ in determining which variables to transform.

Let's now describe the data.

```{r}
df2_f <- df2 %>%
  filter(Sex == "Females")

df2 %>% 
  group_by(Sex) %>% 
  Hmisc::describe(.)
```
# get the descriptive summary between sex
```{r}
df2%>% 
  mutate(log_contrast=log(Contrast_Sensitivity_Threshold),
         log_motion=log(Motion_duration_Threshold)) %>% 
 # select(Sex, log_contrast, log_motion, Mental_Rotation_scores, Vocabulary_scores, Masculine_hobbies,Feminine_hobbies) %>%
  filter(Sex=="Males") %>%
  psych::describe()

df2%>% 
  mutate(log_contrast=log(Contrast_Sensitivity_Threshold),
         log_motion=log(Motion_duration_Threshold)) %>% 
 # select(Sex, log_contrast, log_motion, Mental_Rotation_scores, Vocabulary_scores, Masculine_hobbies,Feminine_hobbies) %>%
  filter(Sex=="Females") %>%
  psych::describe()
```



## T-test: Comparison between Sexes

Here is our pre-registered description of how we planned to compare sex differences:

> To examine sex differences, one-tailed t tests will be conducted to compare men and women on 2 visual perception thresholds, spatial ability, and masculine hobbies. We will use verbal ability as our control variable. We set a family-wise Type I error rate at $\alpha$=0.05. Because there are four dependent variables hypothesized to show sex differences, the critical p value for each sex comparison is 0.0125 after Bonferroni correction. Our goal is to obtain .8 power to detect a medium effect size of .5 (Cohen’s $d$) at the $p$ value of .0125 in the one-tailed t tests. Unequal sample sizes of the two sexes may be collected in this study. The minimum effect size of .50 can be obtained by at least 45 male participants out of a total sample size of 300 (see the R-code for power analysis at WRONG URL! shorturl.at/nDHLV). The minimum detectable effect size decreases when male and female sample sizes differ less, but to simply our $t$ tests, we set the effect sizes at .5.

Since the motion duration and contrast sensitivity theshold scores are not normally distributed, we (log) transform them (see below)

### Vocabulary

```{r}
advoc_total_t <-
  t.test(
    Vocabulary_scores ~ Sex,
    data = df2,
    var.equal = TRUE,
    alternative = "less"
  )
advoc_total_t
advoc_cor_t <-
  t.test(
    Vocabulary_scores_cor_num ~ Sex,
    data = df2,
    var.equal = TRUE,
    alternative = "less"
  )
advoc_cor_t
```

Vocabulary is a control variable in the study. As we predicted, the vocabulary score did not differ between males and females. 

### Mental rotation

```{r}
t.test(
  Mental_Rotation_scores ~ Sex,
  data = df2,
  var.equal = TRUE,
  alternative = "less"
) #Hypothesized
t.test(
  Mental_Rotation_scores_both ~ Sex,
  data = df2,
  var.equal = TRUE,
  alternative = "less"
) #Hypothesized
```

Sex differences in mental rotation test was found in our study. 
Males had significantly more correct answers in the mental rotation task than females. 
This was also the case where we analyzed just the mental rotation items where both correct responses were selected.

### Feminine hobbies

```{r}
t.test(
  Feminine_hobbies ~ Sex,
  data = df2,
  var.equal = TRUE,
  alternative = "greater"
)
```

Although we did not include female-type hobbies in our preregistration, we found that females had higher scores in female-typed hobbies than males. 

### Masculine hobbies

```{r}
t.test(
  Masculine_hobbies ~ Sex,
  data = df2,
  var.equal = TRUE,
  alternative = "less"
) #Hypothesized
```

As predicted, we found males have higher scores in male-typed hobbies than females.

## Transformation

>If necessary, we will transform the psychophysical thresholds to make the distributions symmetric and appropriate for parametric analyses.

For the distributions which are not normal (particularly for distributions that are right skewed), we will try the log transformation. 

### log(Motion duration threshold)

```{r}
shapiro.test(log(df2$Motion_duration_Threshold))
hist(log(df2$Motion_duration_Threshold))
```

Even after the log transformation, `Motion_duration_Threshold` remains non-normal, but it is more symmetric.

```{r}
mdt_tt <-
  t.test(
    log(Motion_duration_Threshold) ~ Sex,
    data = df2,
    var.equal = TRUE,
    alternative = "greater"
  ) #Hypothesized
mdt_tt
```

We found there are sex differences in log(`Motion_duration_Threshold`). 
Males took significantly shorter time to detect the direction of the motion than females. 

### log(Contrast_Sensitivity_Threshold)

```{r}
shapiro.test(log(df2$Contrast_Sensitivity_Threshold))
hist(log(df2$Contrast_Sensitivity_Threshold))
```

`Contrast_Sensitivity_Threshold` remains non-normal even after transformation.

```{r}
t.test(
  log(Contrast_Sensitivity_Threshold) ~ Sex,
  data = df2,
  var.equal = TRUE,
  alternative = "greater"
) #Hypothesized
```

Log transformed `Contrast_Sensitivity_Threshold` data show the predicted sex differences. Males detect the stimuli with lower contrast than females. 

## Power analysis

```{r}
t_power <-
  pwr.t2n.test(
    n1 = 102 ,
    n2 = 30 ,
    d = NULL,
    sig.level = 0.0125,
    power = 0.8,
    alternative = "greater"
  )
t_power
```

We need $|d|>0.65$ for a one-sided t test with $p$ value of lower than 0.0125 and with power of 0.8.

## Correlation within Sex

> To examine how individual differences of visual perception measures are associated with other tasks, we will use correlations within sex. The lower visual perception threshold is, the higher perceptual sensitivity this individual has. In both sexes, we expect to find negative correlations between visual perception measures and spatial ability and masculine hobbies, but no significant correlation with verbal ability. There are four planned correlations (two visual perception tasks × two cognitive tasks) within sex, for a total of eight. This project is a novel study that has not to our knowledge been conducted previously. So we have consciously decided to maintain strict control of Type II error, in order to have enough statistical power to detect a small correlation effect sizes (r=0.20) within the constraints of sample size. This decision to maximize the power (.80) leads to a trade-off between Type I and Type II error. We plan to conduct eight separate one-tailed correlation tests with Type I error at 0.05 and no Bonferroni correction. With a critical p value of .05, around 150 participants are required for each group to detect an effect size of 0.20 at an obtained power of 0.8 with a one-tailed correlation test. 

### Overall

```{r}
meets_criterion <- function(observed_p, criterion_p = .05/4) {
  if (observed_p <= criterion_p) {
    "meets"
  } else {
    "does not meet"
  }
}
```

Because our preregistration envisioned a much larger total sample, we have chosen to report the overall correlations, combining males and females.

We select the variables for our correlation analysis, and make sure to log transform the threshold measures.

```{r}
df_corr <- df2 %>%
  dplyr::mutate(., Motion_duration_Threshold = log(Motion_duration_Threshold),
                Contrast_Sensitivity_Threshold = log(Contrast_Sensitivity_Threshold)) %>%
  dplyr::select(., Sex,
                Contrast_Sensitivity_Threshold,
                Motion_duration_Threshold,
                Mental_Rotation_scores,
                Vocabulary_scores,
              #  Vocabulary_scores_cor_num,
               # Mental_Rotation_scores_both,
                Feminine_hobbies,
                Masculine_hobbies)
```

Then, we drop incomplete cases.

```{r}
df_complete <- df_corr[stats::complete.cases(df_corr),]
```

This gives us $n=$ `r dim(df_complete)[1]` complete cases.

We select just the numeric scores to calculate the correlation table.

```{r}
df_complete_num <- df_complete %>%
  dplyr::select(., -Sex)
```

```{r}
corr_all <- Hmisc::rcorr(as.matrix(df_complete_num), type = c("pearson"))
```

#### Coefficients

```{r}
options(digits=2)
corr_all$r
```

#### P-values

```{r}
corr_all$P
```

```{r}
# Get some colors
col <- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = corr_all$r, col = col, symm = TRUE)
```

#### Observations

- In examining the association between motion duration thresholds and contrast sensitivity thresholds, we find $r=$ `r corr_all$r['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`, $n=$ `r corr_all$n['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`. This `r meets_criterion(corr_all$P['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold'])` criterion for statistical significance.
- In examining the association between between motion duration thresholds and mental rotation, we find $r=$ `r corr_all$r['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $n=$ `r corr_all$n['Motion_duration_Threshold', 'Mental_Rotation_scores']`. This `r meets_criterion(corr_all$P['Motion_duration_Threshold', 'Mental_Rotation_scores'])` criterion for statistical significance.
- In examining the association between motion duration thresholds and vocabulary scores, we find $r=$ `r corr_all$r['Motion_duration_Threshold', 'Vocabulary_scores']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Vocabulary_scores']`, , $n=$ `r corr_all$n['Motion_duration_Threshold', 'Vocabulary_scores']`. This `r meets_criterion(corr_all$P['Motion_duration_Threshold', 'Vocabulary_scores'])` criterion for statistical significance.
- In examining the association between motion duration thresholds and interest in feminine-typed hobbies, we find $r=$ `r corr_all$r['Motion_duration_Threshold', 'Feminine_hobbies']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Feminine_hobbies']`, $n=$ `r corr_all$n['Motion_duration_Threshold', 'Feminine_hobbies']`. This `r meets_criterion(corr_all$P['Motion_duration_Threshold', 'Feminine_hobbies'])` criterion for statistical significance.

- In examining the association between contrast sensitivity thresholds and mental rotation, we find $r=$ `r corr_all$r['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_all$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $n=$ `r corr_all$n['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`. This `r meets_criterion(corr_all$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores'])` criterion for statistical significance.
- In examining the association between contrast sensitivity thresholds and interest in masculine-typed hobbies, we find $r=$ `r corr_all$r['Motion_duration_Threshold', 'Masculine_hobbies']`, $p=$ `r corr_all$P['Motion_duration_Threshold', 'Masculine_hobbies']`, $n=$ `r corr_all$n['Motion_duration_Threshold', 'Masculine_hobbies']`. This `r meets_criterion(corr_all$P['Motion_duration_Threshold', 'Masculine_hobbies'])` criterion for statistical significance.

### Females

Select the females and focus on the numeric scores.

```{r}
df_complete_F <- df_complete %>%
  dplyr::filter(., Sex == 'Females') 

df_corr_F <- df_complete_F %>%
  dplyr::select(., -Sex)

corr_F <- Hmisc::rcorr(as.matrix(df_corr_F), type = c("pearson"))
```

#### Coefficients

```{r}
corr_F$r
```

#### P values

```{r}
corr_F$P
```

```{r}
# Get some colors
col <- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = corr_F$r, col = col, symm = TRUE)
```

#### Observations

- We found a positive association between motion duration thresholds and contrast sensitivity thresholds in females. $r=$ `r corr_F$r['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`, $p<$ `r corr_F$P['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`.
- We found that motion duration threshold is negatively correlated with mental rotation scores in females, $r=$ `r corr_F$r['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_F$P['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`.
This shows that shorter motion duration thresholds (better sensitivity) is correlated with better ability in mental rotation tasks. 
- We found that contrast sensitivity threshold is negatively correlated with mental rotation scores in females, $r=$ `r corr_F$r['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_F$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`. This shows that the lower contrast the participants can detect, the better ability in mental rotation tasks for women. 
- We did not find any relationship between hobbies and the two visual perception tasks 
- Interestingly, we found mental rotation scores are negatively correlated with interest in female-typed hobbies in females, $r=$ `r corr_F$r['Mental_Rotation_scores', 'Feminine_hobbies']`, $p<$ `r corr_F$P['Mental_Rotation_scores', 'Feminine_hobbies']`.

### Males

Select the females and focus on the numeric scores.

```{r}
df_complete_M <- df_complete %>%
  dplyr::filter(., Sex == 'Males') 

df_corr_m <- df_complete_M %>%
  dplyr::select(., -Sex)

corr_M <- Hmisc::rcorr(as.matrix(df_corr_m), type = c("pearson"))
```

#### Coefficients

```{r}
corr_M$r
```

#### P values

```{r}
corr_M$P
```

```{r}
# Get some colors
col <- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = corr_M$r, col = col, symm = TRUE)
```

#### Observations

- We found that motion duration threshold is positively correlated with contrast sensitivity threshold in males, $r=$ `r corr_M$r['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']` $p<$ `r corr_M$P['Motion_duration_Threshold', 'Contrast_Sensitivity_Threshold']`.
- We found a positive correlation between masculine and feminine hobby interests in males, $r=$ `r corr_M$r['Feminine_hobbies', 'Masculine_hobbies']`, $p<$ `r corr_M$P['Feminine_hobbies', 'Masculine_hobbies']`

# Visualization

```{r}
df_corr2<- df3 %>%
  dplyr::mutate(., Motion_duration_Threshold = log(Motion_duration_Threshold),
                Contrast_Sensitivity_Threshold = log(Contrast_Sensitivity_Threshold)) %>%
  dplyr::select(., Sex,
                Contrast_Sensitivity_Threshold,
                Motion_duration_Threshold,
                Mental_Rotation_scores,
                Vocabulary_scores,
              #  Vocabulary_scores_cor_num,
               # Mental_Rotation_scores_both,
                Feminine_hobbies,
                Masculine_hobbies)

df_complete2 <- df_corr2[stats::complete.cases(df_corr2),]
```


```{r}
sex_diff_scatter <-
  function(df,
           x_var,
           y_var,
           x_rev = FALSE,
           y_rev = FALSE,
           an1 = "",
           an2 = "",
           anx = NULL,
           any = NULL,
           square_axis = TRUE) {
    require(tidyverse)
    require(ggExtra)
    
    x_var_s <- sym(x_var)
    y_var_s <- sym(y_var)
    
    p <- ggplot(df) +
      aes(
        x = !!x_var_s,
        y = !!y_var_s,
        group = Sex,
        color = Sex
      ) +
      geom_point() +
      xlab(x_var) +
      ylab(y_var) +
      stat_smooth(method = "lm", na.rm = TRUE) +
      theme_classic2() +
      theme(legend.position = "bottom",
            legend.title = element_blank()) +
      annotate(
        "text",
        x = anx,
        y = any,
        label = c(an1, an2),
        color = c('red', 'darkturquoise')
      )
    
    if (square_axis)
    {
      p + coord_fixed()
    }
    
    if (stringr::str_detect(x_var, 'hobbies')) {
      p <- p + xlim(1, 5)
    }
    if (stringr::str_detect(y_var, 'hobbies')) {
      p <- p + ylim(1, 5)
    }
    
    # Reverse scale for threshold measures?
    if (x_rev)
      p <- p + scale_x_reverse()
    if (y_rev)
      p <- p + scale_y_reverse()
    
    p1 <- ggExtra::ggMarginal(
      p,
      type = "density",
      margins = "both",
      xparams = list(bins = 10),
      yparams = list(bins = 10),
      groupFill = TRUE
    )
    p1
  }
```

```{r sex-diff-corr-sum-function}
sex_diff_corr_summ <- function(x_var, y_var) {
  corr_all_df <- tibble::tibble(
    cor_coef = corr_all$r[x_var, y_var],
    p_val = corr_all$P[x_var, y_var],
    n =  corr_all$n[x_var, y_var],
    pop = "Both"
  )
  males_df <- tibble::tibble(
    cor_coef = corr_M$r[x_var, y_var],
    p_val = corr_M$P[x_var, y_var],
    n =  corr_M$n[x_var, y_var],
    pop = "Males"
  )
  
  females_df <- tibble::tibble(
    cor_coef = corr_F$r[x_var, y_var],
    p_val = corr_F$P[x_var, y_var],
    n =  corr_F$n[x_var, y_var],
    pop = "Females"
  )
  
  df <- rbind(corr_all_df, males_df, females_df)
  
  kableExtra::kable(df, format = 'html') %>%
    kableExtra::kable_styling()
}
```


## Motion duration & Contrast sensitivity

```{r motion-duration-contrast-sens}
sex_diff_scatter(
  df_complete,
  "Motion_duration_Threshold",
  "Contrast_Sensitivity_Threshold",
  x_rev = TRUE,
  y_rev = TRUE,
  "r=0.21*",
  "r=0.54***",
  c(-2.16, -2.16),
  c(-1.4, -1.3)
)

sex_diff_corr_summ("Motion_duration_Threshold",
                   "Contrast_Sensitivity_Threshold")
```

## Motion duration & Mental rotation

```{r motion-duration-mental-rot}
sex_diff_scatter(
  df_complete,
  "Motion_duration_Threshold",
  "Mental_Rotation_scores",
  x_rev = TRUE,
  y_rev = FALSE,
  "r = 0.31**",
  "r = 0.09",
  c(0.17),
  c(24, 33)
)
sex_diff_corr_summ("Motion_duration_Threshold", "Mental_Rotation_scores")
```

<!-- - Overall: $r=$ `r corr_all$r['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Mental_Rotation_scores']` -->
<!-- - Males: $r=$ `r corr_M$r['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_M$P['Motion_duration_Threshold', 'Mental_Rotation_scores']` -->
<!-- - Females: $r=$ `r corr_F$r['Motion_duration_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_F$P['Motion_duration_Threshold', 'Mental_Rotation_scores']` -->

## Motion duration & vocabulary

```{r motion-duration-vocab}
sex_diff_scatter(
  df_complete,
  "Motion_duration_Threshold",
  "Vocabulary_scores",
  x_rev = TRUE,
  y_rev = FALSE,
  "r = 0.18",
  "r=0.22",
  c(0.17),
  c(24, 33)
)
sex_diff_corr_summ("Motion_duration_Threshold", "Vocabulary_scores")
```

<!-- - Overall: $r=$ `r corr_all$r['Motion_duration_Threshold', 'Vocabulary_scores']`, $p<$ `r corr_all$P['Motion_duration_Threshold', 'Vocabulary_scores']` -->
<!-- - Males: $r=$ `r corr_M$r['Motion_duration_Threshold', 'Vocabulary_scores']`, $p<$ `r corr_M$P['Motion_duration_Threshold', 'Vocabulary_scores']` -->
<!-- - Females: $r=$ `r corr_F$r['Motion_duration_Threshold', 'Vocabulary_scores']`, $p<$ `r corr_F$P['Motion_duration_Threshold', 'Vocabulary_scores']` -->

## Contrast sensitivity and Mental rotation

```{r contrast-sens-mental-rot}
sex_diff_scatter(
  df_complete,
  "Contrast_Sensitivity_Threshold",
  "Mental_Rotation_scores",
  x_rev = TRUE,
  y_rev = FALSE,
  "r = -0.19*",
  "r = 0.12",
  c(0.24),
  c(19, 32)
)
sex_diff_corr_summ("Contrast_Sensitivity_Threshold", "Mental_Rotation_scores")
```

<!-- - Overall: $r=$ `r corr_all$r['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_all$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']` -->
<!-- - Males: $r=$ `r corr_M$r['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_M$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']` -->
<!-- - Females: $r=$ `r corr_F$r['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']`, $p<$ `r corr_F$P['Contrast_Sensitivity_Threshold', 'Mental_Rotation_scores']` -->

## Contrast sensitivity & Masculine hobbies

```{r contrast-sens-m-hobbies}
sex_diff_scatter(
  df_complete,
  "Contrast_Sensitivity_Threshold",
  "Masculine_hobbies",
  x_rev = TRUE,
  y_rev = FALSE,
  "r = -0.19*",
  "r = 0.26",
  c(0.24),
  c(2.4, 4)
)
sex_diff_corr_summ("Contrast_Sensitivity_Threshold", "Masculine_hobbies")
```
## Motion duration & Feminine hobbies

```{r}
sex_diff_scatter(
  df_complete,
  "Motion_duration_Threshold",
  "Feminine_hobbies",
  x_rev = TRUE,
  y_rev = FALSE,
  "r = 0.17*",
  "r = -0.01",
  c(0.165),
  c(4, 3)
)
sex_diff_corr_summ("Motion_duration_Threshold", "Feminine_hobbies")
```
<!-- - Overall: $r=$ `r corr_all$r['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']`, $p<$ `r corr_all$P['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']` -->
<!-- - Males: $r=$ `r corr_M$r['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']`, $p<$ `r corr_M$P['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']` -->
<!-- - Females: $r=$ `r corr_F$r['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']`, $p<$ `r corr_F$P['Contrast_Sensitivity_Threshold', 'Masculine_hobbies']` -->

## Masculine and Feminine hobbies

```{r m-hobbies-f-hobbies}
sex_diff_scatter(df_complete, 
                x_var = "Masculine_hobbies",
                y_var = "Feminine_hobbies",
                x_rev = FALSE,
                y_rev = FALSE,
                an1 = "",
                an2 = "",
                anx = 3,
                any = c(1.8, 1.7))
sex_diff_corr_summ("Masculine_hobbies", "Feminine_hobbies")
```

<!-- - Overall: $r=$ `r corr_all$r['Feminine_hobbies', 'Masculine_hobbies']`, $p<$ `r corr_all$P['Feminine_hobbies', 'Masculine_hobbies']` -->
<!-- - Males: $r=$ `r corr_M$r['Feminine_hobbies', 'Masculine_hobbies']`, $p<$ `r corr_M$P['Feminine_hobbies', 'Masculine_hobbies']` -->
<!-- - Females: $r=$ `r corr_F$r['Feminine_hobbies', 'Masculine_hobbies']`, $p<$ `r corr_F$P['Feminine_hobbies', 'Masculine_hobbies']` -->

## Other plots

```{r}
# ggscatter(
#   df2_f,
#   x = "Contrast_Sensitivity_Threshold",
#   y = "Mental_Rotation_scores",
#   add = "reg.line",
#   conf.int = TRUE,
#   cor.coef = TRUE,
#   cor.method = "pearson",
#   xlab = "Contrast sensitivity",
#   ylab = "Mental rotation"
# ) + theme_classic()
```

```{r}
# df2 %>% ggplot(aes(
#   x = log(Motion_duration_Threshold),
#   y = Mental_Rotation_scores,
#   group = Sex,
#   color = Sex
# )) +
#   geom_point() + xlab("log of motion duration (s)") + ylab("contrast sensitivity")
# stat_smooth(method = "lm", na.rm = TRUE)
# 
# library("ggpubr")
# ggscatter(df2_f, x = "Motion_duration_Threshold", y = "Mental_Rotation_scores", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "pearson",
#           xlab = "Motion duration (s)", ylab = "Mental rotation") +theme_classic()
```

## Power analysis

```{r}
# Mental_Rotation_scores and mdt 
r_powerf <-
  pwr.r.test(
    n = 102,
    r = NULL,
    sig.level = 0.05,
    power = 0.8,
    alternative = "greater"
  )
r_powerf
r_powerm <-
  pwr.r.test(
    n = 30,
    r = NULL,
    sig.level = 0.05,
    power = 0.8,
    alternative = "greater"
  )
r_powerm
```

For a sample size of 102, we need |r|>0.24 for one-side t test with p value of lower than 0.05 with the power of 0.8.
As for sample size of 30, we need |r|>0.44 for one-side t test with p value of lower than 0.05 with the power of 0.8.


## correlation
```{r}
df_complete %>% 
  dplyr::select(Sex,Contrast_Sensitivity_Threshold,Motion_duration_Threshold,  Mental_Rotation_scores, Masculine_hobbies,Feminine_hobbies) %>%
  drop_na() %>%
  group_by(Sex) %>%
  corr.test %>%
  print(short = FALSE)

library(ggm)
pcor(c("Contrast_Sensitivity_Threshold", "Motion_duration_Threshold", "Sex"), var(df_complete)) # partial corr between a and b controlling for x, y, z
```

# mediation analysis
```{r}
library(mediation)
# scale the variables 
```

### Feminine_hobbies ->Motion_duration_Threshold->Mental_Rotation_scores
```{r}
# Step #1: The total effect
fit.totaleffect=lm(Mental_Rotation_scores~Feminine_hobbies,df2)
summary(fit.totaleffect) # As you can see, the total effect of f hobbies on our dv is significant (p<.05).
# Step #2: The effect of the IV onto the mediator
# To establish any mediation, the independent variable (iv, “sepal length” in our case) must significantly affect the mediator. This is logical as, without any effect here, no mediation can take place.
fit.mediator=lm(Motion_duration_Threshold~Feminine_hobbies,df2)
summary(fit.mediator) # the total effect of f hobbies on our MRT is significant (p<.05).
# Step #3: The effect of the mediator on the dependent variable
fit.dv=lm(Mental_Rotation_scores~Motion_duration_Threshold+Feminine_hobbies,df2)
summary(fit.dv) # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results = mediate(fit.mediator, fit.dv, treat='Feminine_hobbies', mediator='Motion_duration_Threshold') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results)
# not significant ACME is boot=T
```
>> ACME stands for average causal mediation effects. This is the indirect effect of the IV (sepal length) on the DV (likelihood of pollination) that goes through the mediator (attractiveness to bee). Note that it estimated this effect to be -.50 — this is exactly X (the effect of the IV on the mediator from step #2) times X (the mediator's effect on the DV from step #3) — so not necessarily new information. However, what is new, is that we now have a confidence interval and significance levels for the entire indirect effect, not only its two parts. This is something we need for reporting the mediation.
ADE stands for average direct effects. It describes the direct effect of the IV on the DV. Again — if you’ve been paying attention closely — this is not new information. We have calculated this effect before in step #3: the direct effect of the IV on the DV when controlling for the mediator.
Total Effect stands for the total effect (direct + indirect) of the IV on the DV. This also isn’t new information. We calculated this in step #1. We can also get it by simply adding the ACME (.113) and the ADE (.019) to receive the total effect of .13. We also already knew that the total effect was significant from step #1.
Prop. Mediated describes the proportion of the effect of the IV on the DV that goes through the mediator. It’s calculated by dividing the ACME (-0.50) by the total effect (-3.41) to receive .14. This piece of information is a nice tidbit but not necessarily the focus of our interest.

### Feminine_hobbies ->Mental_Rotation_scores->Motion_duration_Threshold
```{r}
fit.totaleffect=lm(Motion_duration_Threshold~Feminine_hobbies,df2)
summary(fit.totaleffect) 
fit.Y=lm(Motion_duration_Threshold~Mental_Rotation_scores+Feminine_hobbies,df_complete_F)
summary(fit.Y)
fit.M=lm(Mental_Rotation_scores~Feminine_hobbies,df_complete_F)
summary(fit.M) # the total effect of f hobbies on our MRT is significant (p<.05).
# gvlma(fit.M) 
# Step #3: The effect of the mediator on the dependent variable
 # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results1 = mediate(fit.M, fit.Y, treat='Feminine_hobbies', mediator='Mental_Rotation_scores') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results1)
```

###  Motion_duration_Threshold->Mental_Rotation_scores->Feminine_hobbies
```{r}
fit.totaleffect3=lm(Feminine_hobbies~Motion_duration_Threshold,df2)
summary(fit.totaleffect3) 
fit.Y3=lm(Feminine_hobbies~Mental_Rotation_scores+Motion_duration_Threshold,df2)
summary(fit.Y3)
fit.M3=lm(Mental_Rotation_scores~Motion_duration_Threshold,df2)
summary(fit.M3) # the total effect of f hobbies on our MRT is significant (p<.05).
# gvlma(fit.M) 
# Step #3: The effect of the mediator on the dependent variable
 # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results3 = mediate(fit.M3, fit.Y3, treat='Motion_duration_Threshold', mediator='Mental_Rotation_scores') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results3)
```

###  Motion_duration_Threshold->Feminine_hobbies->Mental_Rotation_scores
```{r}
fit.totaleffect4=lm(Mental_Rotation_scores~Motion_duration_Threshold,df2)
summary(fit.totaleffect4) 
fit.Y4=lm(Mental_Rotation_scores~Feminine_hobbies+Motion_duration_Threshold,df2)
summary(fit.Y4)
fit.M4=lm(Feminine_hobbies~Motion_duration_Threshold,df2)
summary(fit.M4) # the total effect of f hobbies on our MRT is significant (p<.05).
# gvlma(fit.M) 
# Step #3: The effect of the mediator on the dependent variable
 # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results4 = mediate(fit.M4, fit.Y4, treat='Motion_duration_Threshold', mediator='Feminine_hobbies') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results4)
```
### Masculine_hobbies ->Contrast_Sensitivity_Threshold->Mental_Rotation_scores
```{r}
# Step #1: The total effect
fit.totaleffect2=lm(Mental_Rotation_scores~Masculine_hobbies,df2)
summary(fit.totaleffect2) # As you can see, the total effect of f hobbies on our dv is significant (p<.05).
# Step #2: The effect of the IV onto the mediator
# To establish any mediation, the independent variable (iv, “sepal length” in our case) must significantly affect the mediator. This is logical as, without any effect here, no mediation can take place.
fit.m2=lm(Contrast_Sensitivity_Threshold~Masculine_hobbies,df2)
summary(fit.m2) # the total effect of f hobbies on our MRT is significant (p<.05).
# Step #3: The effect of the mediator on the dependent variable
fit.y2=lm(Mental_Rotation_scores~Contrast_Sensitivity_Threshold+Masculine_hobbies,df2)
summary(fit.y2) # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results2 = mediate(fit.m2, fit.y2, treat='Masculine_hobbies', mediator='Contrast_Sensitivity_Threshold') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results2)
# not significant ACME is boot=T
```

###  Contrast_Sensitivity_Threshold->Masculine_hobbies->Mental_Rotation_scores
```{r}
fit.totaleffect=lm(Mental_Rotation_scores~Contrast_Sensitivity_Threshold,df2)
summary(fit.totaleffect) 
fit.Y5=lm(Mental_Rotation_scores~Masculine_hobbies+Contrast_Sensitivity_Threshold,df2)
summary(fit.Y5)
fit.M5=lm(Masculine_hobbies~Contrast_Sensitivity_Threshold,df2)
summary(fit.M5) # the total effect of f hobbies on our MRT is significant (p<.05).
# gvlma(fit.M) 
# Step #3: The effect of the mediator on the dependent variable
 # The mediator has a significant effect (p<.05) on the dv. 
# Step #4: Causal Mediation Analysis
results5 = mediate(fit.M5, fit.Y5, treat='Contrast_Sensitivity_Threshold', mediator='Masculine_hobbies') # Also, we need to specify boot=T as, by default, mediate will use a quasi-Bayesian approximation for confidence intervals. However, we want to report percentile confidence intervals, so we set it to T for true. 
summary(results5)
```